---
title: "Table 1"
output: html_document
date: "2025-05-07"
---

```{r,include=FALSE}
library(tidyverse)
library(tableone)
library(writexl)
library(gtsummary)
library(survival)
library(ggplot2)
library(readxl)
library(ggpubr)
library(splines)
library(xlsx)
library(lattice)
library(mice)
library(DescTools)
library(survminer)
library(finalfit)
library(tidycmprsk)
library(ggsurvfit) 
library(sqldf)
library(table1)
library(cobalt)



pen <- read_csv("~/Partners HealthCare Dropbox/Tianqi Ouyang/De-identified Data/PEN/Harmony_DATA_2025-02-20_0757(sevda.aghayeva@pennmedicine.upenn.edu)_JR.csv") %>% select(order(colnames(.))) %>% mutate(id = paste0("pen_", row_number()))

mmc <- read_csv('/Users/to909/Partners HealthCare Dropbox/Tianqi Ouyang/De-identified Data/MMC/HepatorenalSyndromeA_DATA_2025-01-30_1528(pamejia@montefiore.org)_JR.csv') %>%  select(order(colnames(.)))%>% mutate(id = paste0("mmc_", row_number()))

csf <- read_csv('/Users/to909/Partners HealthCare Dropbox/Tianqi Ouyang/De-identified Data/CSF/TerlipressinStudy_DATA_2025-03-20_1346_JR.csv') %>% select(order(colnames(.)))%>% mutate(id = paste0("csf_", row_number()))




unm <- read_csv('/Users/to909/Partners HealthCare Dropbox/Tianqi Ouyang/De-identified Data/UNM/HRSHarmonyTerlipress_DATA_2025-02-10_2216(jteixeira@salud.unm.edu)_JR.csv')%>% select(order(colnames(.)))%>% mutate(id = paste0("unm_", row_number()))

bid <- read_csv('/Users/to909/Partners HealthCare Dropbox/Tianqi Ouyang/De-identified Data/BID/Data Export 2025.02.05(wyang8@bidmc.harvard.edu)_JR.csv')%>% select(order(colnames(.)))%>% mutate(id = paste0("bid_", row_number()))

bsw <- read_csv('/Users/to909/Partners HealthCare Dropbox/Tianqi Ouyang/De-identified Data/BSW/TerlipressinRegistry_DATA_2025-03-12_0744_JR.csv')%>% select(order(colnames(.)))%>% mutate(id = paste0("bsw_", row_number()))

ccf <- read_csv('/Users/to909/Partners HealthCare Dropbox/Tianqi Ouyang/De-identified Data/CCF/HARMONY_ClevelandClinic_HRSData Updated_Queries 04FEB2025(mehkrio@ccf.org)_JR.csv')%>% select(order(colnames(.)))%>% mutate(id = paste0("ccf_", row_number()))


cpm <- read_csv('/Users/to909/Partners HealthCare Dropbox/Tianqi Ouyang/De-identified Data/CPM/HARMONYHRSFrederick_DATA_2025-03-03_1134(mary.thornton@sutterhealth.org)_JR.csv')%>% select(order(colnames(.)))%>% mutate(id = paste0("cpm_", row_number()))


och <- read_csv('/Users/to909/Partners HealthCare Dropbox/Tianqi Ouyang/De-identified Data/OCH/OCHHRSTerlipressinRe_DATA_2025-01-02_2259(gavin.skipper@ochsner.org)_JR.csv')%>% select(order(colnames(.)))%>% mutate(id = paste0("och_", row_number()))

nwm <- read_csv('/Users/to909/Partners HealthCare Dropbox/Tianqi Ouyang/De-identified Data/NWM/02282025 NWM Terli Data(anjana.rajan@nm.org)_JR.csv')%>% select(order(colnames(.)))%>% mutate(id = paste0("nwm_", row_number()))

mgh <- read_csv('/Users/to909/Partners HealthCare Dropbox/Tianqi Ouyang/De-identified Data/MGH/TerlipressinDatabase_DATA_2025-04-15_1219.csv')%>% select(order(colnames(.)))%>% mutate(id = paste0("mgh_", row_number()))

yal <- read_csv('/Users/to909/Partners HealthCare Dropbox/Tianqi Ouyang/De-identified Data/YAL/TerlipressinForHepat_DATA_2025-02-08_1107_JR.csv')%>% select(order(colnames(.)))%>% mutate(id = paste0("yal_", row_number()))


mcm <- read_csv('/Users/to909/Partners HealthCare Dropbox/Tianqi Ouyang/De-identified Data/MCM/HepatorenalSyndromeT_DATA_2025-02-20_0828(kusztos.victoria@mayo.edu)_JR.csv')%>% select(order(colnames(.)))%>% mutate(id = paste0("mcm_", row_number()))

inu <- read_csv('/Users/to909/Partners HealthCare Dropbox/Tianqi Ouyang/De-identified Data/INU/TerlipressinDatabase_DATA_2025-02-13_1416(esorman@iu.edu)_JR.csv')%>% select(order(colnames(.)))%>% mutate(id = paste0("inu_", row_number()))


mayo <- read_csv('/Users/to909/Partners HealthCare Dropbox/Tianqi Ouyang/De-identified Data/Mayo/HepatorenalSyndromeT_DATA_2025-03-22_1749(vargas.hugo@mayo.edu)_JR.csv')%>% select(order(colnames(.)))%>% mutate(id = paste0("mayo_", row_number()))


#Function to get common variables and missing variables in each dataframe
get_common_and_missing_variables <- function(...) {
  # Get the list of dataframes
  dfs <- list(...)
  
  # Get the names of the dataframes (for labeling)
  args <- match.call(expand.dots = FALSE)$`...`
  df_names <- sapply(args, deparse)
  
  # List of column names for each dataframe
  df_cols <- lapply(dfs, names)
  
  # Find common columns across all dataframes
  common_cols <- Reduce(intersect, df_cols)
  
  # Get all unique columns from all dataframes
  all_cols <- unique(unlist(df_cols))
  
  # Find missing columns in each dataframe
  missing_cols <- lapply(df_cols, function(cols) setdiff(all_cols, cols))
  
  # Name the list elements with dataframe names
  names(missing_cols) <- df_names
  
  # Return the results as a list
  return(list(common_variables = common_cols, missing_variables = missing_cols))
}



  

bid <- bid %>% select(-c("gihep_consult_date","neph_consult_date",  "pall_consult_date" ))
pen <- pen %>% select(-c("gihep_consult_date", "neph_consult_date",  "pall_consult_date" ))
yal <- yal %>% select(-c("gihep_consult_date", "neph_consult_date",  "pall_consult_date" ))
mcm <- mcm %>% select(-c("gihep_consult_date", "neph_consult_date",  "pall_consult_date","redcap_data_access_group" ))

mayo <- mayo %>% select(-c("gihep_consult_date", "neph_consult_date", "pall_consult_date","redcap_data_access_group" ))

vars <- get_common_and_missing_variables(bid, bsw, ccf, cpm, csf,inu, mayo, mcm, mgh, mmc, nwm, och, pen, unm, yal)


vars$missing_variables


reorder_and_bind <- function(data_list) {
  # 1) For each data frame, reorder columns based on sorted column names
  data_list_reordered <- lapply(data_list, function(df) {
    df %>% dplyr::select(order(colnames(df)))
  })
  
  # 2) Row-bind (rbind) all data frames into one
  combined_df <- do.call(rbind, data_list_reordered)
  return(combined_df)
}

df_list <- list(bid, bsw, ccf, cpm, csf,inu, mayo, mcm, mgh, mmc, nwm, och, pen, unm, yal)

all<- reorder_and_bind(df_list)




# new variable function 

child_pugh_score <- function(tbili, albumin, inr, ascites, hegrade) {
  # Bilirubin Score
  childpugh_bili <- ifelse(tbili < 2, 1,
                      ifelse(tbili >= 2 & tbili <= 3, 2, 3))
  
  # Albumin Score
  childpugh_alb <- ifelse(albumin > 3.5, 1,
                     ifelse(albumin >= 2.8 & albumin <= 3.5, 2, 3))
  
  # INR Score
  childpugh_inr <- ifelse(inr < 1.7, 1,
                     ifelse(inr >= 1.7 & inr <= 2.3, 2, 3))
  
  # Ascites Score (assuming values: 1 = absent, 2 = slight, 3 = moderate)
  childpugh_ascites <- ifelse(ascites == 1, 1,
                         ifelse(ascites == 2, 2, 3))
  
  # Hepatic Encephalopathy Score (assuming values: 0 = none, 1-2 = mild, 3-4 = severe)
  childpugh_he <- ifelse(hegrade == 0, 1,
                    ifelse(hegrade %in% c(1, 2), 2, 3))
  
  # Final Child-Pugh Score
  childpugh_total <- childpugh_bili + childpugh_alb + childpugh_inr + childpugh_ascites + childpugh_he
  
  return(childpugh_total)
}




# estimate_creatinine <- function(egfr, age, sex) {
#   # Define constants based on CKD-EPI 2021 equation
#   if (sex == 1) {
#     k <- 0.9
#     alpha <- -0.302
#     sex_factor <- 1  # No adjustment for males
#   } else {
#     k <- 0.7
#     alpha <- -0.241
#     sex_factor <- 1.012  # Adjustment factor for females
#   }
#   
#   # Compute creatinine using the inverse of the race-free CKD-EPI equation
#   creatinine <- (egfr / (142 * min(1, k)^alpha * max(1, k)^-1.2 * 0.9938^age * sex_factor))^(1 / -1.2)
#   
#   return(creatinine)
# }


estimate_creatinine <- function(egfr, age, sex) {
  
  # Set parameters based on sex
  if (sex == 1) { # male
    A <- 0.9
    sex_factor <- 1
  } else { # female
    A <- 0.7
    sex_factor <- 1.012
  }

  # Define a minimization function to find the creatinine
  estimated_creatinine <- function(Scr) {
    B <- ifelse(Scr <= A,
                ifelse(sex == 1, -0.302, -0.241),
                -1.2)
    calculated_egfr <- 142 * (Scr / A)^B * (0.9938^age) * sex_factor
    return((calculated_egfr - egfr)^2)
  }

  # Use optimize to find Scr that minimizes the squared error
  result <- optimize(estimated_creatinine, interval = c(0.1, 2.5))
  
  return(result$minimum)
}



calculate_clif_c_score <- function(tb_admit, peak_creatinine, he_grade_admission, inr_admit, map, pressor, fio2_admission, spo2_admission, age_admission, wbc_admit) {
  
  clif_score <- 0
  
  # TB Admit Score
  clif_score <- clif_score + case_when(
    is.na(tb_admit) ~ 0,
    tb_admit < 6 ~ 1,
    tb_admit >= 6 & tb_admit < 12 ~ 2,
    tb_admit >= 12 ~ 3,
    TRUE ~ 0
  )
  
  # Peak Creatinine Score
  clif_score <- clif_score + case_when(
    is.na(peak_creatinine) ~ 0,
    peak_creatinine < 2 ~ 1,
    peak_creatinine >= 2 & peak_creatinine < 3.5 ~ 2,
    peak_creatinine >= 3.5 ~ 3,
    TRUE ~ 0
  )
  
  # HE Grade Admission Score
  clif_score <- clif_score + case_when(
    is.na(he_grade_admission) ~ 0,
    he_grade_admission == 1 ~ 1,
    he_grade_admission %in% c(2, 3) ~ 2,
    he_grade_admission %in% c(4, 5) ~ 3,
    TRUE ~ 0
  )
  
  # INR Admit Score
  clif_score <- clif_score + case_when(
    is.na(inr_admit) ~ 0,
    inr_admit < 2 ~ 1,
    inr_admit >= 2 & inr_admit < 2.5 ~ 2,
    inr_admit >= 2.5 ~ 3,
    TRUE ~ 0
  )
  
  # MAP and Pressor Score
  clif_score <- clif_score + case_when(
    is.na(map) ~ 0,
    map >= 70 & pressor != 1 ~ 1,
    map < 70 & pressor != 1 ~ 2,
    !is.na(map) & pressor == 1 ~ 3,
    TRUE ~ 0
  )
  
  # FIO2 and SPO2 Admission Score
  if (!is.na(fio2_admission)) {
    ratio <- spo2_admission / fio2_admission
    clif_score <- clif_score + case_when(
      ratio > 357 ~ 1,
      ratio > 214 & ratio <= 357 ~ 2,
      ratio <= 214 ~ 3,
      TRUE ~ 0
    )
  }
  
  # Calculate CLIF-C Score
  CLIF_C_Score <- 10 * (0.33 * clif_score + 0.04 * age_admission + 0.63 * log(wbc_admit) - 2)
  
  return(CLIF_C_Score)
}



calculate_organ_failures <- function(bili_terli_day0, he_terli_day0, inr_terli_day0, 
                                     map_terli_values, fio2_terli_day0, 
                                     spo2_terli_day0, scr_terli_day0) {
  
  # Initialize organ failure flags
  liver_f <- 0
  brain_f <- 0
  coagulation_f <- 0
  circulatory_f <- 0
  respiratory_f <- 0
  kidney_f <- 0
  
  # Apply conditions
  if (!is.na(bili_terli_day0) && bili_terli_day0 >= 6) {
    liver_f <- 1
  }
  
  if (!is.na(he_terli_day0) && he_terli_day0 > 1) {
    brain_f <- 1
  }
  
  if (!is.na(inr_terli_day0) && inr_terli_day0 >= 2) {
    coagulation_f <- 1
  }
  
  # Calculate mean MAP (if any MAP values are provided) and compare
  if (!is.na(map_terli_values) && map_terli_values < 70) {
    circulatory_f <- 1
  }
  
  # Check respiratory condition using SpO2/FiO2 ratio
  if (!is.na(fio2_terli_day0) && fio2_terli_day0 != 0 && 
      !is.na(spo2_terli_day0) && (spo2_terli_day0 / fio2_terli_day0) <= 357) {
    respiratory_f <- 1
  }
  
  if (!is.na(scr_terli_day0) && scr_terli_day0 >= 1.5) {
    kidney_f <- 1
  }
  
  # Return the results as a list
  return(sum(
    liver_f , 
    brain_f, 
    coagulation_f, 
    circulatory_f, 
    respiratory_f, 
    kidney_f
  ))
}


# create discont_terli_day
discont_terli_days <- grep("discont_terli_day", str_sort(names(all)), value = TRUE)
discont_terli_day_numbers <- as.numeric(sub(".*_day(\\d+)$", "\\1", discont_terli_days))
sorted_discont_terli <- discont_terli_days[order(discont_terli_day_numbers)]


# create scr_day
scr_days <- grep("^scr_.*_day(0|[1-9]|1[0-3])$", str_sort(names(all)), value = TRUE)
day_numbers <- as.numeric(sub(".*_day(\\d+)$", "\\1", scr_days))
sorted_scr <- scr_days[order(day_numbers)]


# other variables 
selected_variables <- tolower(c( "dc_available_albumin___999", 
    "dc_available_inr___999",
    "dc_available_scr___999",
    "dc_available_sna___999",
    "dc_available_tbili___999","dc_albumin", "dc_inr", "dc_scr", "dc_sna", "dc_tbili",
  "Hrsreversal", "Age", "sex_male", "Race", "Hispanic",
  "Cirrhosis_etiology",

"Scr_admit",

"Tbili_admit",

"Inr_admit",

"Sodium_admit",

"Albumin_admit",

"baseline_scr",

"baseline_scr_days_to_admit", 	

"baseline_scr",
"scr_day1_post_terli",
"scr_day2_post_terli",
"scr_day3_post_terli",

"dc_lt_90days",
"dc_hd_status",
"dc_scr90_value",
"aki_height",
"aki_weight"


))


  scr_vars <- c(
    "scr_admit", "baseline_scr", "baseline_scr_120to365_value", "scr_aki",
    "scr_terli_day0", "scr_terli_day1", "scr_terli_day2", "scr_terli_day3", 
    "scr_terli_day4", "scr_terli_day5", "scr_terli_day6", "scr_terli_day8", 
    "scr_terli_day9", "scr_terli_day10", "scr_terli_day11", "scr_terli_day12", 
    "scr_terli_day13", "scr_day1_post_terli", "scr_day2_post_terli", "scr_day3_post_terli", 
    "peakhospit_scr", "nadirhospit_scr", 
    "dc_scr", "dc_scr30_value", "dc_scr60_value", "dc_scr90_value", 
    "scr_value_1yr", "scr_value_day_of_ua_cr_hrs"
  )

  
  # Total bilirubin (T. bili)
  bili_vars <- c(
    "tbili_admit", "tbili_aki",
    "bili_terli_day0", "bili_terli_day1", "bili_terli_day2", "bili_terli_day3",
    "bili_terli_day4", "bili_terli_day5", "bili_terli_day6", "bili_terli_day7",
    "bili_terli_day8", "bili_terli_day9", "bili_terli_day10", "bili_terli_day11",
    "bili_terli_day12", "bili_terli_day13",
    "dc_tbili"
  )

  
  # INR: 
  inr_vars <- c(
    "inr_admit", "inr_aki",
    "inr_terli_day0", "inr_terli_day1", "inr_terli_day2", "inr_terli_day3",
    "inr_terli_day4", "inr_terli_day5", "inr_terli_day6", "inr_terli_day7",
    "inr_terli_day8", "inr_terli_day9", "inr_terli_day10", "inr_terli_day11",
    "inr_terli_day12", "inr_terli_day13",
    "dc_inr"
  )

  
  # Albumin: 
  alb_vars <- c(
    "albumin_admit", "albumin_aki",
    "alb_terli_day0", "alb_terli_day1", "alb_terli_day2", "alb_terli_day3",
    "alb_terli_day4", "alb_terli_day5", "alb_terli_day6", "alb_terli_day7",
    "alb_terli_day8", "alb_terli_day9", "alb_terli_day10", "alb_terli_day11",
    "alb_terli_day12", "alb_terli_day13",
    "dc_albumin"
  )

  
  # Sodium (Na):
  na_vars <- c(
    "sodium_admit", "sodium_aki", "sna_value_day_of_ua_na_hrs",
    "na_terli_day0", "na_terli_day1", "na_terli_day2", "na_terli_day3",
    "na_terli_day4", "na_terli_day5", "na_terli_day6", "na_terli_day7",
    "na_terli_day8", "na_terli_day9", "na_terli_day10", "na_terli_day11",
    "na_terli_day12", "na_terli_day13",
    "dc_sna"
  )

# ,all_of(selected_variables)
all_selected <- all %>% select(id,subjectid,all_of(sorted_discont_terli),all_of(sorted_scr),dc_death_90days,days_to_discharge,dc_days_lastencounter,dc_days_to_death,days_to_lost_to_followup,all_of(selected_variables),"dc_death_90days",
    "days_to_discharge",
    "dc_days_lastencounter",
    "dc_days_to_death",
    "days_to_lost_to_followup",
    "scr_day1_post_terli",
"scr_day2_post_terli",
"scr_day3_post_terli",
"peakhospit_scr",
"rrt",
"dc_lt_90days",
"dc_hd_status",
"dc_scr90_value",
"dc_terli_use","dc_available_albumin___999", 
    "dc_available_inr___999",
    "dc_available_scr___999",
    "dc_available_sna___999",
    "dc_available_tbili___999",
"dc_albumin", "dc_inr", "dc_scr", "dc_sna", "dc_tbili")

# a <- all %>% mutate(# 0, No | 1, Yes | 2, Lost to follow up
#                  time_90=case_when(dc_death_90days==0 ~ days_to_discharge+dc_days_lastencounter,
#                                     dc_death_90days==1 ~ days_to_discharge+dc_days_to_death,
#                                     dc_death_90days==2 ~ days_to_discharge+days_to_lost_to_followup
#                                     )) %>% select(time_90,dc_death_90days,days_to_discharge,dc_days_lastencounter,dc_days_to_death,days_to_lost_to_followup)
# 
# a <- qc_check(test)
# a1 <- test %>% merge(a,by="subjectid",all.x = T) %>% mutate(# 0, No | 1, Yes | 2, Lost to follow up
#                  time_90=case_when(dc_death_90days==0 ~ days_to_discharge+dc_days_lastencounter,
#                                     dc_death_90days==1 ~ days_to_discharge+dc_days_to_death,
#                                     dc_death_90days==2 ~ days_to_discharge+days_to_lost_to_followup
#                                     )) %>% select(time_90,dc_death_90days,days_to_discharge,dc_days_lastencounter,dc_days_to_death,days_to_lost_to_followup,Checking )
# 



```





#qc_check (correct)
```{r,include=FALSE}

qc_check<- function(data) {
  # Initialize vectors to store results
  id <- character()
  checking <- character()
  discont_day <- numeric()
  
  # Columns related to availability and their corresponding DC columns
  dc_available_cols <- c(
    "dc_available_albumin___999", 
    "dc_available_inr___999",
    "dc_available_scr___999",
    "dc_available_sna___999",
    "dc_available_tbili___999"
  )
  dc_cols <- c("dc_albumin", "dc_inr", "dc_scr", "dc_sna", "dc_tbili")
  
  # Get column names for discontinuation and SCr days
  discont_cols <- grep("^discont_terli_day", names(data), value = TRUE)
  scr_cols <- grep("^scr_terli_day", names(data), value = TRUE)
  
  # Other columns (exclude subjectid, discont columns, scr columns, and DC columns)
  other_cols <- setdiff(
    names(data),
    c("subjectid", discont_cols, scr_cols, dc_available_cols, dc_cols,# Add these to exclude them from other_cols
    "dc_death_90days",
    "days_to_discharge",
    "dc_days_lastencounter",
    "dc_days_to_death",
    "days_to_lost_to_followup",
    "scr_day1_post_terli",
"scr_day2_post_terli",
"scr_day3_post_terli",
"peakhospit_scr",
"rrt",
"dc_lt_90days",
"dc_hd_status",
"dc_scr90_value",
"dc_terli_use"
)
  )
  
  # Loop through each row in the dataset
  for (i in seq_len(nrow(data))) {
    
    current_id <- data$subjectid[i]
    
    # Extract values for "discont_terli_day" columns
    discont_values <- data[i, discont_cols, drop = FALSE]
    discont_names <- names(discont_values)
    
    # Extract values for "scr_terli_day" columns
    scr_values <- data[i, scr_cols, drop = FALSE]
    scr_names <- names(scr_values)
    
    # Extract values for other variables
    other_values <- data[i, other_cols, drop = FALSE]
    other_names <- names(other_values)
    
    # Temporary storage for the current row
    current_checking <- character()
    current_discont_day <- NA
    
    # --- 1) Identify the discontinuation day --------------------------------
    for (j in seq_along(discont_values)) {
      col_value <- discont_values[[j]]
      
      if (!is.na(col_value) && col_value == 1) {
        # Extract the day number from the column name, e.g. "discont_terli_day5" -> 5
        current_discont_day <- as.numeric(
          gsub("discont_terli_day", "", discont_names[j])
        )
        break
      } else if (is.na(col_value)) {
        # If the value is NA, add the column name to current_checking
        current_checking <- c(current_checking, discont_names[j])
      }
    }
    
    # --- 2) Check SCr columns up to the discontinuation day -----------------
    if (!is.na(current_discont_day)) {
      # If a discontinuation day was found, only check up to that day’s column
      # Example: if day=5, we check scr_terli_day0 through scr_terli_day5
      cols_to_check <- seq_len(current_discont_day + 1)  # day0-based indexing
      cols_to_check <- cols_to_check[cols_to_check <= ncol(scr_values)]
      
      scr_subset_values <- scr_values[, cols_to_check, drop = FALSE]
      scr_subset_names <- names(scr_subset_values)
      
      # Flag missing SCr in that subset
      for (k in seq_along(scr_subset_values)) {
        if (is.na(scr_subset_values[[k]])) {
          current_checking <- c(current_checking, scr_subset_names[k])
        }
      }
    } else {
      # If we have no discontinuation day, check all SCr columns for missing
      for (k in seq_along(scr_values)) {
        if (is.na(scr_values[[k]])) {
          current_checking <- c(current_checking, scr_names[k])
        }
      }
    }
    
    # --- 3) Check the availability columns and their corresponding DC columns
    for (m in seq_along(dc_available_cols)) {
      avail_val <- data[[dc_available_cols[m]]][i]
      
      # If availability is NA => flag both availability col & dc_* col
      if (is.na(avail_val)) {
        current_checking <- c(
          current_checking, 
          dc_available_cols[m],  # e.g. "dc_available_albumin___999"
          dc_cols[m]             # e.g. "dc_albumin"
        )
        next
      }
      
      # If availability is 0 => the corresponding dc_* should not be NA
      if (avail_val == 0) {
        dc_value <- data[[dc_cols[m]]][i]
        if (is.na(dc_value)) {
          # We expected a value here, but it's missing
          current_checking <- c(current_checking, dc_cols[m])
        }
      }
    }
    
    # --- 4) Check other variables for missing values ------------------------
    for (l in seq_along(other_values)) {
      if (is.na(other_values[[l]])) {
        current_checking <- c(current_checking, other_names[l])
      }
    }
    
    # --- 5) Simplified logic for dc_death_90days checks ---------------------
    # For dc_death_90days = 0, 1, or 2, we only check two variables each time.
    dc_death_90days_val <- data[["dc_death_90days"]][i]
    days_to_discharge_val <- data[["days_to_discharge"]][i]
    dc_days_lastencounter_val <- data[["dc_days_lastencounter"]][i]
    dc_days_to_death_val <- data[["dc_days_to_death"]][i]
    days_to_lost_to_followup_val <- data[["days_to_lost_to_followup"]][i]
    
    # Check if dc_death_90days or days_to_discharge is NA
   if (is.na(dc_death_90days_val) || is.na(days_to_discharge_val)) {
      current_checking <- c(
        current_checking, 
        "dc_death_90days", 
        "days_to_discharge",
        "dc_days_lastencounter",
        "dc_days_to_death",
        "days_to_lost_to_followup"
      )
    } 
    # If dc_death_90days is not NA, check the relevant pair of variables
    else  {
      if (dc_death_90days_val == 0) {
        # Must check: days_to_discharge (already done above) + dc_days_lastencounter
        if (is.na(dc_days_lastencounter_val)) {
          current_checking <- c(current_checking, "dc_days_lastencounter")
        }
      } 
      else if (dc_death_90days_val == 1) {
        # Must check: days_to_discharge (already done above) + dc_days_to_death
        if (is.na(dc_days_to_death_val)) {
          current_checking <- c(current_checking, "dc_days_to_death")
        }
      } 
      else if (dc_death_90days_val == 2) {
        # Must check: days_to_discharge (already done above) + days_to_lost_to_followup
        if (is.na(days_to_lost_to_followup_val)) {
          current_checking <- c(current_checking, "days_to_lost_to_followup")
        }
      }
    }
    
    # --- 6) Store results if any issues or we have a Discont_Day -------------
    if (length(current_checking) > 0 || !is.na(current_discont_day)) {
      id <- c(id, current_id)
      checking <- c(checking, paste(current_checking, collapse = ", "))
      discont_day <- c(discont_day, current_discont_day)
    }
  }
  
  # Combine the results into a data frame
  results <- data.frame(
    subjectid = id, 
    Checking = checking, 
    Discont_Day = discont_day,
    stringsAsFactors = FALSE
  )
  
  # Return the results
  return(results)
}


```



# Final data 1
```{r,include=FALSE}
qc_check_data <- qc_check(all_selected)
final_master <- all %>% merge(qc_check_data %>% select(subjectid,Discont_Day),all.x = T,by="subjectid") 

# Create the Removed_id vector
removed_id <- c(
  "BID-PTD-001", "BID-PTD-002", "BID-PTD-003", "BID-PTD-004", "BID-PTD-005", 
  "BID-PTD-006", "BID-PTD-007", "MAYO-5", "MAYO-6", "MAYO-7", "MAYO-8", 
  "MAYO-9", "MAYO-10", "MAYO-11", "MAYO-12", "MAYO-13", "MAYO-14", 
  "MAYO-15", "MAYO-16", "MAYO-17", "MAYO-18", "MAYO-19", "MAYO-20", 
  "MAYO-21", "MAYO-22", "MAYO-23", "MAYO-24", "MAYO-25", "MAYO-26", 
  "MAYO-27", "MAYO-28", "MMC-005", "MMC-006", "MMC-007"
)

# Create the Subgroup_id vector
subgroup_id <- c(
  "BID-005R1", "BID-005R2", "BID-013R1", "MGH-001R1", "MGH-014R1", 
  "MGH-014R2", "MGH-026R1", "NWM-014R1"
)

subgroup_master <- final_master %>% filter(subjectid %in% subgroup_id)
final_master <- final_master %>% filter(!subjectid %in% removed_id,!subjectid %in% subgroup_id)





#### 1 final_master


df_long <- final_master %>% 
  pivot_longer(
    cols = starts_with("map_terli_day"), 
    names_to = c("temp", "day", "time"),    # we will capture these parts
    names_pattern = "^(map_terli)_day(\\d+)_time(\\d+)$", # regex to split
    values_to = "map"
  ) %>%
  # 2) Convert day/time to numeric so we can sort properly
  mutate(
    day = as.numeric(day),
    time = as.numeric(time)
  ) %>%
  select(-temp)  # 'temp' is just the literal "map_terli", can drop if not needed

# 3) Calculate the mean for each ID and day (across times 0–3, etc.)
df_summary <- df_long %>%
  group_by(subjectid, day) %>%
  summarise(
    mean_map = mean(map, na.rm = TRUE),
    sd_map   = sd(map, na.rm = TRUE),
    .groups  = "drop"
  )
map <- df_summary %>% filter(day==0) %>% select(subjectid,mean_map) %>% rename(mean_map_day0=mean_map)

dosechange_days  <- grep("dosechange_terli_day", str_sort(names(all)), value = TRUE)
dosechange_days_numbers <- as.numeric(sub(".*_day(\\d+)$", "\\1", dosechange_days))
sorted_dosechange_days <- dosechange_days[order(dosechange_days_numbers)]
sorted_dosechange_days <- sorted_dosechange_days[sorted_dosechange_days != "dosechange_terli_day1"]



create_dosechange_day <- function(df) {
  df$dosechange_day <- apply(df, 1, function(row) {
    for (i in 2:13) {
      varname <- paste0("dosechange_terli_day", i)
      if (!is.na(row[[varname]]) && row[[varname]] == 1) {
        return(i)
      }
    }
    return(NA)  # Return NA if no change is found
  })
  return(df)
}

final_master <- create_dosechange_day(final_master)
test <- create_dosechange_day(final_master %>% select(sorted_dosechange_days))
# table1(~as.factor(dosechange_day),final_master)

# time to death 

ckd_epi_gfr <- function(creat, male, age) {
  k <- ifelse(male == 1, 0.9, 0.7)
  a <- ifelse(male == 1, -0.302, -0.241)
  m <- ifelse(male == 1, 1, 1.012)
  
  ratio <- creat / k
  
  gfr <- 142 * 
         (pmin(ratio, 1))^a * 
         (pmax(ratio, 1))^-1.2 * 
         0.9938^age * 
         m
  
  return(gfr)
}

# 
# days_to_discharge > 90days  
# 
#      1.disposition(death 5 alive: other )     dc_death_90days: 
# time_to_death-days_to_terli_initiation_day0: 1.days_to_discharge(death ) 2.time = days_to_discharge + dc_days_to_death 3.days_to_discharge +days_to_lost_to_followup 
# status_death: 1.disposition(discharge)       2.dc_death_90days=1.  3. disposition != 5 & dc_death_90days=2  
# select(disposition,dc_death_status,days_to_discharge,dc_death_90days,after_discharge_90days_death_status,dc_days_to_death,days_to_terli_initiation_day0 ) 

final_master <- final_master %>% mutate(
  dc_death_status=if_else(disposition==5,1,0),
  after_discharge_90days_death_status=if_else(dc_death_90days==1,1,0),
  dc_days_to_death=if_else(dc_death_90days==2|dc_death_90days==0,90,dc_days_to_death)
  ) %>% 
  mutate(
    days_to_lost_to_followup =if_else(is.na(days_to_lost_to_followup),0,days_to_lost_to_followup),
  time_to_death=case_when(
    dc_death_status==1 ~ days_to_discharge,
    dc_death_status==0 & dc_death_90days==2~ days_to_discharge+days_to_lost_to_followup,
    dc_death_status==0 & dc_death_90days!=2~  days_to_discharge+dc_days_to_death
  )) %>% 
  mutate(time_to_death_status=case_when(dc_death_status==1 ~ 1,
                                               dc_death_status==0 & after_discharge_90days_death_status==1 ~ 1,
                                               TRUE ~0)) %>% mutate(time_to_death=time_to_death-days_to_terli_initiation_day0)


```


# Final data 2
```{r,include=FALSE}
final_master <- final_master %>% 
  filter(!is.na(Discont_Day)) %>%
  # filter(scr_terli_day0>=1.5) %>% 
  rowwise() %>% 
  mutate(
    last_scr = get(paste0("scr_terli_day", Discont_Day)),  # Extract last SCr based on discontinuation day
    last_scr_2= get(paste0("scr_terli_day", Discont_Day-1)),
    discont_reason_terli = get(paste0("discont_reason_terli_day", Discont_Day)),
    terli_ae_abdpain = get(paste0("terli_ae_abdpain_day", Discont_Day)),
    terli_ae_nausea = get(paste0("terli_ae_nausea_day", Discont_Day)),
    terli_ae_diarrhea = get(paste0("terli_ae_diarrhea_day", Discont_Day)),
    terli_ae_volover = get(paste0("terli_ae_volover_day", Discont_Day)),
    terli_ae_brady = get(paste0("terli_ae_brady_day", Discont_Day)),
    terli_other = get(paste0("terli_other_day", Discont_Day))
  ) %>% 
  merge(map,by="subjectid",all.x = T) %>% 
  # lowest_creatinine
  mutate(lowest_creatinine=pmin(last_scr_2, last_scr, scr_day1_post_terli, na.rm = TRUE)) %>% 
  # HRS_reversal_new
  mutate(HRS_reversal_new = case_when(
          lowest_creatinine <= 1.5 & (scr_terli_day0 - lowest_creatinine) >= 0.3 ~ 1,  # HRS_reversal = 1
          TRUE ~ 0  )) %>%  
  
  mutate(scr_terli_day0=ifelse(scr_terli_day0>100,scr_terli_day0/100,scr_terli_day0),
        fio2_terli_day0=ifelse(fio2_terli_day0 > 1,fio2_terli_day0/100,fio2_terli_day0)) %>% 
  
  # transplant_lt
  mutate(transplant_lt=
        case_when(lt_during_hospital == 1 | slkt_during_hospital== 1 ~ 1,
              dc_lt_90days == 1 | dc_lt_90days == 2 ~ 2,
              lt_during_hospital == 0 & lt_status_1yr == 1 & days_to_lt_1yr > 90 ~ 3,
              TRUE ~ 0),
        time_to_transplant = case_when(
          transplant_lt == 1 & !is.na(days_to_lt) ~ days_to_lt,
          transplant_lt == 1 & is.na(days_to_lt) ~ days_to_discharge - days_to_lt_1yr,
          transplant_lt==2 | transplant_lt== 3 ~ days_to_discharge+days_to_lt_1yr,
          TRUE ~ NA_real_),
        time_to_transplant =time_to_transplant -days_to_terli_initiation_day0) %>% 
  mutate(transplant_lt_status=if_else(transplant_lt==0,0,2)) %>%
           mutate(time_to_transplant_cmp=if_else(is.na(time_to_transplant),999,time_to_transplant)) %>% 
  # transplant_slkt
  mutate(transplant_slkt=case_when(slkt_during_hospital == 1|dc_lt_90days == 2 | lt_type_1yr == 2 ~ 1,
                                   TRUE ~ 0)) %>% 
  # baseline_scr_calculated and baseline_scr_new
  mutate(
    egfr=75,
    baseline_scr_calculated=mapply(estimate_creatinine, egfr, age, sex_male),
    baseline_scr_new = case_when(baseline_scr_days_to_admit != 0 & !is.na(baseline_scr) ~ baseline_scr,
                                 baseline_scr_days_to_admit == 0 & !is.na(baseline_scr_120to365_value)~ baseline_scr_120to365_value,
                                 baseline_scr_days_to_admit == 0 & is.na(baseline_scr_120to365_value) ~ pmin(baseline_scr_calculated,scr_admit)),
      baseline_scr_new_2 = case_when(baseline_scr_days_to_admit != 0 & !is.na(baseline_scr) ~ baseline_scr,
                                 baseline_scr_days_to_admit == 0 & !is.na(baseline_scr_120to365_value)~ baseline_scr_120to365_value),
      eGFR=mapply(ckd_epi_gfr, baseline_scr_new_2,sex_male,age ))%>% 
 # ratio and delta for akin 
   mutate(ratio=round(scr_terli_day0 / baseline_scr_new,4),
         delta=round(scr_terli_day0 - baseline_scr_new,4),
         akin = case_when(( ratio>=1.5 & ratio < 2) | (ratio<1.5 & delta >0.3 )~ 1,
                          (ratio >= 2 & ratio < 3) ~ 2,
                          ratio >= 3  ~ 3, # check 3.0
                           TRUE ~ NA),
         akin = ifelse(scr_terli_day0>=4,3,akin)) %>% 
  # first non NA 
  mutate(bili_cal=coalesce(bili_terli_day0, tbili_admit, mean(bili_terli_day0,na.rm = T))) %>% 
  # clif_c_score
  mutate(clif_c_score= mapply(calculate_clif_c_score, tbili_admit, scr_terli_day0, he_terli_day0, 
                       inr_terli_day0, map_terli_day0_time0, norepi_terli_day0, fio2_terli_day0, spo2_terli_day0, 
                       age, wbc_terli_day0)) %>% 
  # aclf_grade
  mutate(aclf_grade= mapply(calculate_organ_failures,bili_terli_day0, he_terli_day0, inr_terli_day0, 
                                     map_terli_day0_time0, fio2_terli_day0, 
                                     spo2_terli_day0, scr_terli_day0)) %>% 
  # child_pugh_score
  mutate(child_pugh_score=mapply(child_pugh_score,bili_terli_day0, alb_terli_day0, inr_terli_day0, ascites_aki, he_terli_day0)) %>%  
  
  # discont_ratio and delta
  mutate(
    discont_ratio=round(lowest_creatinine / baseline_scr_new,4),
    discont_delta= round( lowest_creatinine - baseline_scr_new,4),
 # discont_aki_stage
    discont_aki_stage = case_when(
      is.na(discont_ratio) | is.na(discont_delta) ~ NA_real_,
      discont_ratio < 1.5 & discont_delta < 0.3 ~ 0,
      
      (discont_ratio >= 1.5 & discont_ratio < 2) |  (discont_ratio < 1.5 & discont_delta >= 0.3 )~ 1,
      
      discont_ratio >= 2 & discont_ratio < 3 ~ 2,
      
      discont_ratio >= 3   ~ 3),
    discont_aki_stage = ifelse(lowest_creatinine >=4,3,discont_aki_stage),
 
    difference = round(akin - discont_aki_stage,0),
    # 3) AKI_responders classification
 
    hrs_responders = case_when(
      # is.na(akin) | is.na(lowest_creatinine) ~ "Missing",
      difference <= 0 ~ 0,
      difference > 0 & round(lowest_creatinine - baseline_scr_new,2) > 0.3 ~ 1,
      round(lowest_creatinine - baseline_scr_new,2) <=0.3  ~ 2),
 
    hrs_responders_cat_2 =ifelse(hrs_responders==0,0,1)) 



  final_master <- final_master %>% 
  mutate(
    creatinine_adj_day0 = case_when(
      scr_terli_day0 < 1 ~ 1,
      scr_terli_day0 >= 4 ~ 4,
      TRUE ~ scr_terli_day0
    ),
    day0_meld = round(9.57 * log(creatinine_adj_day0) + 3.78 * log(bili_terli_day0) + 11.20 * log(inr_terli_day0) + 6.43),
    day0_meld_na = round(day0_meld + 1.32 * (137 - pmin(pmax(na_terli_day0, 125), 137)) - (0.033 * day0_meld * (137 - pmin(pmax(na_terli_day0, 125), 137)))),
    day0_meld_na = ifelse(day0_meld > 11, day0_meld_na, NA), # MELDNa applied only if MELD > 11
    female_factor = if_else(sex_male == 0, 1.33, 0), # Assuming a column 'sex' is present, adjust accordingly
    day0_meld_3 = round(
      female_factor +
      4.56 * log(bili_terli_day0) +
      0.82 * (137 - na_terli_day0) -
      0.24 * (137 - na_terli_day0) * log(bili_terli_day0) +
      9.09 * log(inr_terli_day0) +
      11.14 * log(creatinine_adj_day0) +
      1.85 * (3.5 - alb_terli_day0) -
      1.83 * (3.5 - alb_terli_day0) * log(creatinine_adj_day0) +
      6
    ),
    admit_creatinine_adj= case_when(
      scr_admit < 1 ~ 1,
      scr_admit >= 4 ~ 4,
      TRUE ~ scr_admit
    ),
    admit_meld = round(9.57 * log(admit_creatinine_adj) + 3.78 * log(tbili_admit) + 11.20 * log(inr_admit) + 6.43),
    admit_meld_na = round(admit_meld + 1.32 * (137 - pmin(pmax(sodium_admit, 125), 137)) - (0.033 * admit_meld * (137 - pmin(pmax(sodium_admit, 125), 137)))),
    admit_meld_na = ifelse(admit_meld > 11, admit_meld_na, NA), # MELDNa applied only if MELD > 11
    female_factor = if_else(sex_male == 0, 1.33, 0), # Assuming a column 'sex' is present, adjust accordingly
    admit_meld_3 = round(
      female_factor +
      4.56 * log(tbili_admit) +
      0.82 * (137 - sodium_admit) -
      0.24 * (137 - sodium_admit) * log(tbili_admit) +
      9.09 * log(inr_admit) +
      11.14 * log(admit_creatinine_adj) +
      1.85 * (3.5 - albumin_admit) -
      1.83 * (3.5 - albumin_admit) * log(admit_creatinine_adj) +
      6
    ))%>%mutate(
    liver_f = ifelse(!is.na(bili_terli_day0) & bili_terli_day0 >= 6, 1, 0),
    brain_f = ifelse(!is.na(he_terli_day0) & he_terli_day0 > 1, 1, 0),
    coagulation_f = ifelse(!is.na(inr_terli_day0) & inr_terli_day0 >= 2, 1, 0),
    circulatory_f = ifelse(!is.na(map_terli_day0_time0) & map_terli_day0_time0 < 70, 1, 0),
    respiratory_f = ifelse(
      !is.na(fio2_terli_day0) & fio2_terli_day0 != 0 &
      !is.na(spo2_terli_day0) & (spo2_terli_day0 / fio2_terli_day0) <= 357,
      1, 0
    ),
    kidney_f = ifelse(!is.na(scr_terli_day0) & scr_terli_day0 >= 1.5, 1, 0),
    organ_failure_sum = liver_f + brain_f + coagulation_f + circulatory_f + respiratory_f + kidney_f
  ) %>% mutate(rrt_2=ifelse(rrt==2,0,rrt)) %>% mutate(aclf_grade=if_else(aclf_grade>3,3,aclf_grade)) %>% 
  
  
  # criteria
  mutate(
    criteria_1 = ifelse((total_terli_day1 == 0 | is.na(total_terli_day1)) & discont_terli_day1 == 1, 1, 0),
    criteria_2 = ifelse(aclf_grade >= 3, 1, 0),
    criteria_3 = ifelse(scr_terli_day0 >= 5, 1, 0),
    criteria_4 = case_when(spo2_terli_day0 /fio2_terli_day0 <357 ~1,
                           spo2_terli_day0 /fio2_terli_day0 >=357 ~0),
    criteria_4 =ifelse(is.na(criteria_4),0,criteria_4),
    criteria_5 =ifelse(admit_meld_3>35,1,0), # updated 01/28
    HRS_criteria_meld=if_else((criteria_2 == 1 | criteria_3 == 1 | criteria_4 == 1|criteria_5),1,0),# updated 01/28
    HRS_criteria_3 = if_else((criteria_2 == 1 | criteria_3 == 1 | criteria_4 == 1),1,0),
  
    
  #  HRS_Criteria
    HRS_Criteria = case_when(
      criteria_1 == 0 & criteria_2 == 0 & criteria_3 == 0 & criteria_4 == 0 ~ 0,
      criteria_1 == 1 | criteria_2 == 1 | criteria_3 == 1 | criteria_4 == 1 ~ 1 ))
   
    
    
 final_master <- final_master %>% rowwise() %>%  # Ensure row-wise operations
  mutate(
    last_scr = get(paste0("scr_terli_day", Discont_Day)),  
    
    discont_reason_terli = get(paste0("discont_reason_terli_day", Discont_Day)),
    terli_ae_abdpain = get(paste0("terli_ae_abdpain_day", Discont_Day)),
    terli_ae_nausea = get(paste0("terli_ae_nausea_day", Discont_Day)),
    terli_ae_diarrhea = get(paste0("terli_ae_diarrhea_day", Discont_Day)),
    terli_ae_volover = get(paste0("terli_ae_volover_day", Discont_Day)),
    terli_ae_brady = get(paste0("terli_ae_brady_day", Discont_Day))) %>% 
   mutate(terli_7 =if_else(discont_reason_terli==7,1,0),
               terli_8 =if_else(discont_reason_terli==8,1,0)) %>% 
   mutate(terli_ae_respfail=if_else(terli_7==1|terli_ae_volover==1,1,0)) %>%
    mutate(across(
      c(terli_ae_abdpain, terli_ae_nausea, terli_ae_diarrhea, 
        terli_ae_volover, terli_ae_brady,terli_7,terli_8,terli_ae_respfail),
      ~ if_else(is.na(.x), 0, .x)
    )) %>%  mutate(
    any_ae = if_else(
      terli_ae_abdpain == 1 | terli_ae_nausea == 1 | terli_ae_diarrhea == 1 | 
      terli_ae_volover == 1 | terli_ae_brady == 1 | terli_7 == 1 | 
      terli_8 == 1 | terli_ae_respfail == 1,
      1,  # if any condition is TRUE, set to 1
      0   # else, set to 0
    )
  ) %>% mutate(listed_transplant=if_else(lt_eval==2 | lteval_listingstatus==1,1,0),listed_transplant=ifelse(is.na(listed_transplant),0,listed_transplant)) 
 


 
 dosechange_cols <- c("dosechange_terli_day2", "dosechange_terli_day3",
                     "dosechange_terli_day4", "dosechange_terli_day5",
                     "dosechange_terli_day6", "dosechange_terli_day7",
                     "dosechange_terli_day8", "dosechange_terli_day9",
                     "dosechange_terli_day10", "dosechange_terli_day11",
                     "dosechange_terli_day12")

 final_master <- final_master %>% 
  rowwise() %>%
  mutate(
    dosechange_status = if_else(any(c_across(all_of(dosechange_cols)) == 1, na.rm = TRUE), 1, 0),
    time_to_dosechange = if_else(
      dosechange_status == 1, 
      min(which(c_across(all_of(dosechange_cols)) == 1)) + 1,  # +1 to account for the start at day2
      NA_integer_
    )
  ) %>%
  ungroup()
 

 
 

 
final_master <- final_master %>% 
   mutate(time_to_death_90days=case_when(time_to_death_status==1 & time_to_death <= 90 ~ time_to_death,
                                         time_to_death_status==1 & time_to_death > 90 ~ 90,
                                         time_to_death_status==0 & time_to_death <= 90 ~ time_to_death,
                                         time_to_death_status==0 & time_to_death > 90 ~ 90), 
          time_to_death_status_90days=case_when(time_to_death_status==1 & time_to_death <= 90 ~ 1,
                                         time_to_death_status==1 & time_to_death > 90 ~ 0,
                                         time_to_death_status==0 & time_to_death <= 90 ~ 0,
                                         time_to_death_status==0 & time_to_death > 90 ~ 0),
    
           time_to_transplant_90days=case_when(transplant_lt_status==2 & time_to_transplant_cmp <= 90 ~ time_to_transplant_cmp,
                                         transplant_lt_status==2 & time_to_transplant_cmp > 90 ~ 90,
                                         transplant_lt_status==0 & time_to_transplant_cmp <= 90 ~ time_to_transplant_cmp,
                                         transplant_lt_status==0 & time_to_transplant_cmp > 90 ~ 90),
          time_to_transplant_status_90days=case_when(transplant_lt_status==2 & time_to_transplant_cmp <= 90 ~ 2,
                                         transplant_lt_status==2 & time_to_transplant_cmp > 90 ~ 0,
                                         transplant_lt_status==0 & time_to_transplant_cmp <= 90 ~ 0,
                                         transplant_lt_status==0 & time_to_transplant_cmp > 90 ~ 0),
                   time_to_death_90days_cmp=pmin(time_to_death_90days,time_to_transplant_90days),
                time_to_death_status_90days_cmp=case_when(time_to_death_90days<=time_to_transplant_90days ~ time_to_death_status_90days,
                                                          time_to_death_90days>time_to_transplant_90days ~ time_to_transplant_status_90days)
          
          ) 
            
   
final_master <- final_master %>% mutate(fena=(100 * (scr_admit * ua_na_value_hrs) / (sodium_admit * ua_cr_value_hrs)),
                                        urine_pc=uaprotein_hrs/ua_cr_value_hrs) %>% 
  mutate(hrs_rebound=if_else(scr_day1_post_terli - last_scr >=0.3,1,0)) %>% 
  mutate(admit_meld_3_raw=admit_meld_3) %>% 
  mutate(admit_meld_3 = if_else(
    is.na(admit_meld_3),
    median(admit_meld_3, na.rm = TRUE),
    admit_meld_3
  )) %>% mutate(race_2=if_else(race==1|is.na(race),1,0),hispanic=if_else(is.na(hispanic),0,hispanic)) %>% mutate(transplant_outcome=if_else(time_to_transplant_status_90days==2,1,0)) %>% mutate(ckd_baseline=if_else(eGFR<60,1,0)) %>%   
  mutate(total_albumin = rowSums(
    select(., albumintotal_terli_day0, albumintotal_terli_day1, 
           albumintotal_terli_day2, albumintotal_terli_day3,
           albumintotal_terli_day4, albumintotal_terli_day5,
           albumintotal_terli_day6, albumintotal_terli_day7,
           albumintotal_terli_day8, albumintotal_terli_day9,
           albumintotal_terli_day10, albumintotal_terli_day11,
           albumintotal_terli_day12, albumintotal_terli_day13),
    na.rm = TRUE
  ))
  

final_master <- final_master %>% mutate(clif_c_score_new=if_else(is.na(clif_c_score),median(clif_c_score,na.rm=T),clif_c_score))

```




```{r,include=FALSE}
# Vector of categorical variables



categorical_vars <- c(
  "admit_admitservice",
  "admit_admitroute",
  "sex_male",
  "race",
  "hispanic",
  "insurance_type",
  "cirrhosis_etiology",
  "etoh_hepatitis",
  "hegrade_admit",
  "admit_ascites",
  "htn_medical_hx",
  "dm_medical_hx",
  "ckd_medical_hx",
  "cad_medical_hx",
  "nsbb_preadmission",
  "nsbb_type_preadmission",
  "ace_arb_preadmission",
  "nsaid_preadmission",
  "diuretics_preadmission",
  "sbp_ppx_preadmission",
  "lactulose_preadmission",
  "rifaximin_preadmission",
  "mido_preadmission",
  "ascites_previous_comp",
  "refascites_previous_comp",
  "he_previous_comp",
  "sbp_previous_comp",
  "nonsbp_previous_comp",
  "phtn_bleed_previous_comp",
  "hcc_previous_comp",
  "tips_previous_comp",
  "baseline_scr_outpt",
  "aki_previous_90days",
  "transfer_aki",
  "aki_precipitant_nsbpinf",
  "he_aki",
  "rrt_aki",
  "mv_aki",
  "pressors_aki",
  "chest_imaging",
  "chest_imaging_pulmedema",
  "chest_imaging_effusion",
  "ecg",
  "echo",
  "albumin_before_terli",
  "crystalloid_before_terli",
  "nsbb_before_terli",
  "mido_before_terli",
  "oct_before_terli",
  "ne_before_terli",
  "gihep_consult",
  "neph_consult",
  "pall_consult",
  "code_status",
  "ua_hrs",
  "ua_na_hrs",
  "ua_cr_hrs",
  "ua_urea_hrs",
  "ua_granularcasts_hrs",
  "ua_epi_cells_hrs",
  "location_terli_day0",
  "terli_route_day0",
  "tele_terli_day0",
  "he_terli_day0",
  "infection_terli_day0",
  "typeinfection_terli_day0",
  "hrs_responders",
  "dosechange_terli_day1",
  "dosechange_terli_day2",
  "dosechange_terli_day3",
  "dosechange_terli_day4",
  "dosechange_terli_day5",
  "dosechange_terli_day6",
  "dosechange_terli_day7",
  "dosechange_terli_day8",
  "dosechange_terli_day9",
  "dosechange_terli_day10",
  "dosechange_terli_day11",
  "dosechange_terli_day12",
  "discont_aki_stage",
  "aclf_grade",
  "HRS_Criteria",
  "criteria_1",
  "criteria_2",
  "criteria_3",
  "criteria_4",
  "akin",
  "transplant_slkt",
  "transplant_lt",
  "rrt",
  "rrt_2",
  "rrt_modality",
  "rrt_continuous",
  "hd_discharge",
  "disposition",
  "liver_f",
  "brain_f",
  "coagulation_f",
  "circulatory_f",
  "respiratory_f",
  "kidney_f",
  "baseline_scr_120to365",
  "aki_events_previous90days",
  "prbc_trans_before_terli",
  "time_to_death_status",
   "terli_ae_abdpain", 
    "terli_ae_nausea" ,
    "terli_ae_diarrhea" ,
    "terli_ae_volover" ,
    "terli_ae_brady" ,
    "terli_7",
    "terli_8",
  "terli_ae_respfail","any_ae","listed_transplant","dosechange_status","hrs_rebound","race_2","HRS_reversal_new",
  "hrs_responders_cat_2","time_to_death_status_90days","time_to_death_status_90days_cmp","ckd_baseline","HRS_criteria_3"
)


# Vector of numerical variables
numerical_vars <- c(
  "age",
  "scr_admit",
  "tbili_admit",
  "inr_admit",
  "sodium_admit",
  "albumin_admit",
  "lactate_admit",
  "nsbb_dose_preadmission",
  "mido_dose_preadmission",
  "baseline_scr",
  "baseline_scr_days_to_admit",
 

  "transfer_aki_days_toadmit",
  "days_admit_to_aki",
  "aki_weight",
  "aki_height",
  "aki_hr",
  "aki_sbp",
  "aki_dbp",
  "aki_map",
  "aki_pao2",
  "fio2_aki",
  "scr_aki",
  "bun_aki",
  "albumin_aki",
  "inr_aki",
  "wbc_aki",
  "plt_aki",
  "ecg_qtc",
  "days_to_echo",
  "echo_ef",
  "echo_lateral_e",
  "echo_trpeak",
  "echo_gls",
  "echo_earatio",
  "echo_rvsp",
  "echo_pasp",
  "echo_lavi",
  "echo_tr",
  "totalalbumin_before_terli",
  "albvolume_before_terli",
  "saline_vol_before_terli",
  "lr_volume_before_terli",
  "other_cryst_before_terli",

  "prbc_qaunt_before_terli",
  "totalvolume_before_terli",
  "total_uo_before_terli",
  "days_first_mido_before_terli",
  "days_total_mido_before_terli",
  "mido_maxdose_before_terli",
  "days_first_oct_before_terli",
  "days_total_oct_before_terli",
  "oct_maxdose_before_terli",
  "days_first_ne_before_terli",
  "days_total_ne_before_terli",
  "days_to_gihep_consult",
  "days_to_neph_consult",
  "days_to_pall_consult",
  "days_ua_hrs",
  "days_ua_na_hrs",
  "ua_na_value_hrs",
  "days_ua_cr_hrs",
  "ua_cr_value_hrs",
  "days_ua_urea_hrs",
  "ua_urea_value_hrs",
  "feurea_hrs",
  "ua_rbc_hrs",
  "uaprotein_hrs",
  "temp_terli_day0",
  "hr_terli_day0",
  "pao2_terli_day0",
  "fio2_terli_day0",
  "sbp_terli_day0_time0",
  "map_terli_day0_time0",
  "chloride_terli_day0",
  "bicarb_terli_day0",
  "scr_terli_day0",
  "bun_terli_day0",
  "ast_terli_day0",
  "alt_terli_day0",
  "bili_terli_day0",
  "alb_terli_day0",
  "inr_terli_day0",
  "wbc_terli_day0",
  "hgb_terli_day0",
  "Discont_Day",
  "na_terli_day0",
  "days_to_terli_initiation_day0",
  "clif_c_score",
  "admit_meld",
  "admit_meld_na",
  "admit_meld_3",
  "admit_meld_3_raw",
  "day0_meld",
  "day0_meld_na",
  "day0_meld_3",
  
  "time_to_transplant",
  "time_to_death_status",
  "time_to_death_90days",
  "cystatinc_admit","cystatinc_aki","cystatinc_terli_day0",
  "urine_pc","fena","fena_hrs","time_to_death_90days","total_albumin","mido_maxdose_before_terli "
)


all_vars <- c(numerical_vars,categorical_vars)

final_master$mido_maxdose_before_terli <- as.numeric(final_master$mido_maxdose_before_terli)
final_master <- final_master %>% mutate_at(categorical_vars,as.factor)

# write.xlsx(as.data.frame(final_master),"/Users/to909/Desktop/Terlipressin/final_master_0508.xlsx",showNA = F,row.names= F)
# write.xlsx(as.data.frame(final_master),"/Users/to909/Desktop/Terlipressin/final_master_01282026.xlsx",showNA = F,row.names= F)
```



# Table 1 HRS_reversal_new
```{r,echo=FALSE,warning=FALSE,message=FALSE}

create_table_one <- function(all_vars,
                             cat_vars,
                             data,
                             strata,
                             output) {
  
  numerical_vars=setdiff(all_vars,cat_vars)
  
  # 1) Generate the table
  T1_after <- tableone::CreateTableOne(
    vars       = all_vars,
    strata     = strata,        # variable to stratify by
    data       = data,
    factorVars = cat_vars,      # specify which variables are factors
    addOverall = TRUE,
    includeNA  = FALSE
  )

  # 2) Print TableOne object and convert to data frame
  T1_after_print <-
    print(
      T1_after,
      showAllLevels = T,
      nonnormal = numerical_vars,
      missing       = TRUE,
      quote         = FALSE,
      noSpaces      = TRUE,
      printToggle   = FALSE
    )
  

  # 3) Write the table as CSV
  write.csv(T1_after_print, file = output)
}



```

# table1_check_0508_HRS_reversal_new
```{r,include=FALSE,message=FALSE,echo=FALSE}

all_vars <- unique(all_vars)
categorical_vars <- unique(categorical_vars)

create_table_one(
  all_vars = all_vars,
  cat_vars = categorical_vars,
  data     = final_master,
  strata   = "HRS_reversal_new",
  output   = "/Users/to909/Desktop/Tables/table1_check_0508_HRS_reversal_new.csv"
)


```

# table1_check_0508_hrs_responders
```{r,include=FALSE,message=FALSE,echo=FALSE}

create_table_one(
  all_vars = all_vars,
  cat_vars = categorical_vars,
  data     = final_master,
  strata   = "hrs_responders",
  output   = "/Users/to909/Desktop/Tables/table1_check_0508_hrs_responders.csv"

)



```




# table1_check_0508_hrs_responders_cat_2
```{r,include=FALSE,message=FALSE,echo=FALSE}

create_table_one(
  all_vars = all_vars,
  cat_vars = categorical_vars,
  data     = final_master,
  strata   = "hrs_responders_cat_2",
  output   = "/Users/to909/Desktop/Tables/table1_check_0508_hrs_responders_cat_2.csv"
)


```

# table1_time_to_death_status_90days
```{r,include=FALSE,message=FALSE,echo=FALSE}

create_table_one(
  all_vars = all_vars,
  cat_vars = categorical_vars,
  data     = final_master,
  strata   = "time_to_death_status_90days",
  output   = "/Users/to909/Desktop/Tables/table1_check_0508_time_to_death_status_90days.csv"
)


```

# table1_check_0508_HRS_criteria_3
```{r,include=FALSE,message=FALSE,echo=FALSE}

create_table_one(
  all_vars = all_vars,
  cat_vars = categorical_vars,
  data     = final_master,
  strata   = "HRS_criteria_3",
  output   = "/Users/to909/Desktop/Tables/table1_check_0508_HRS_criteria_3.csv"
)


```



# followup HRS_reversal_new
```{r,include=FALSE,message=FALSE,echo=FALSE}

followup_variables<- c(
  "dc_aki_recurrence",
  "dc_aki_recurrence_number",
  "dc_aki_recurrence_date",
  "days_to_aki_recurrence",
  "dc_aki_recurrence_eitology",
  # "dc_aki_recurrence_etiology_other",
  "dc_terli_use",
  "dc_terli_use_date",
  "dc_days_to_terli_use",
  "dc_hd_status",
  "dc_death_90days",
  "dc_lastecounter_date",
  "dc_days_lastencounter",
  "dc_death90_date",
  "dc_days_to_death",
  "dc_lost_to_followup_date",
  "days_to_lost_to_followup",
  "dc_lt_90days",
  "dc_lt90_date",
  "dc_days_lt",
  "dc_hdstatus_lt",
  "dc_lt_evalsafetynet",
  "dc_lt_safetynetreason",
  "dc_lt_safetynetreasonother",
  "dc_lt_listedsafetynet",
  "dc_lt_safetynetktdate",
  "dc_lt_daystosafetynetkt",
  "dc_90scr_notavailable_lt",
  "dc_scr_90day_postlt_value",
  "dc_scr_90day_postlt_date",
  "dc_days_to_90dayscr_lt",
  "dc_neph_followup",
  "dc_neph_followup_date",
  "dc_days_to_neph_followup",
  "dc_gihep_followup",
  "dc_gihep_followup_date",
  "dc_days_to_gihep_followup",
  "dc_30scr_notavailable",
  "dc_scr30_value",
  "dc_scr_30days_date",
  "dc_days_scr30",
  "dc_60scr_notavailable",
  "dc_scr60_value",
  "dc_scr_60days_date",
  "dc_days_scr60",
  "dc_90scr_notavailable",
  "dc_scr90_value",
  "dc_scr_90days_date",
  "dc_days_scr91",
  "vital_status_1yr",
  "last_encounter_1yr",
  "days_to_last_encounter_1yr",
  "date_death_1yr",
  "days_to_death_1yr",
  "date_lastencounter_1yr",
  "days_lastencounter_1yr",
  "hd_status_1yr",
  "scr_available_1yr",
  "scr_value_1yr",
  "scr_date_1yr",
  "days_to_scr_1yr",
  "lt_status_1yr",
  "lt_type_1yr",
  "lt_date_1yr",
  "days_to_lt_1yr",
  "tips_1yr",
  "tips_1yr_indication",
  "tips_1yr_other",
  "tips_1yr_date"
)

# Remove variables containing the word "date"
followup_variables <- followup_variables[!grepl("date", followup_variables, ignore.case = TRUE)]

# Exclude elements from followup_variables that are in setdiff(followup_variables, all)
followup_variables <- setdiff(followup_variables, setdiff(followup_variables, names(final_master)))


# Identify variables in followup_variables that are completely NA in the dataframe all
completely_na_vars <- followup_variables[sapply(all[followup_variables], function(x) all(is.na(x)))]

# Exclude elements from followup_variables that are in setdiff(followup_variables, all)
followup_variables <- setdiff(followup_variables, completely_na_vars)


# setdiff(followup_variables,all)
# Create a vector with the specified variable names
cat_followup_variables <-  c(
  "dc_aki_recurrence", 
  # "days_to_aki_recurrence", 
  "dc_aki_recurrence_eitology", 
  # "dc_aki_recurrence_etiology_other", 
  "dc_terli_use", 
  # "dc_days_to_terli_use", 
  "dc_hd_status", 
  "dc_death_90days", 
  "dc_lt_90days", 
  "dc_lt_90days", 
  "dc_lt_evalsafetynet", 
  "dc_lt_safetynetreason", 
  "dc_lt_safetynetreasonother", 
  "dc_lt_listedsafetynet", 
  "dc_lt_daystosafetynetkt", 
  "dc_neph_followup", 
  "dc_gihep_followup", 
  "vital_status_1yr", 
  "hd_status_1yr", 
  "lt_status_1yr", 
  "lt_type_1yr", 
  "tips_1yr", 
  "tips_1yr_indication", 
  "tips_1yr_other", 
  "tips_1yr_days",
  "dc_hdstatus_lt"
)

followup_variables <- unique(followup_variables)
cat_followup_variables <- unique(cat_followup_variables)
num_followup_variables <- setdiff(followup_variables,cat_followup_variables)


final_master <- final_master %>% mutate_at(cat_followup_variables,as.factor)


```

# HRS_reversal_new
```{r,include=FALSE}
create_table_one(
  all_vars = followup_variables,
  cat_vars = cat_followup_variables,
  data     = final_master,
  strata   = "HRS_reversal_new",
  output   = "/Users/to909/Desktop/Tables/table_followup_0508_HRS_reversal_new.csv"
)

```
# hrs_responders
```{r,include=FALSE}
create_table_one(
  all_vars = followup_variables,
  cat_vars = cat_followup_variables,
  data     = final_master,
  strata   = "hrs_responders",
  output   = "/Users/to909/Desktop/Tables/table_followup_0508_hrs_responders.csv"
)

```
# hrs_responders_cat_2
```{r,include=FALSE}
create_table_one(
  all_vars = followup_variables,
  cat_vars = cat_followup_variables,
  data     = final_master,
  strata   = "hrs_responders_cat_2",
  output   = "/Users/to909/Desktop/Tables/table_followup_0508_hrs_responders_cat_2.csv"
)

```

# HRS_criteria_3
```{r,include=FALSE}
create_table_one(
  all_vars = followup_variables,
  cat_vars = cat_followup_variables,
  data     = final_master,
  strata   = "HRS_criteria_3",
  output   = "/Users/to909/Desktop/Tables/table_followup_0508_HRS_criteria_3.csv"
)

```


# time_to_death_status_90days
```{r,include=FALSE}
create_table_one(
  all_vars = followup_variables,
  cat_vars = cat_followup_variables,
  data     = final_master,
  strata   = "time_to_death_status_90days",
  output   = "/Users/to909/Desktop/Tables/table_followup_0508_hrs_time_to_death_status_90days.csv"
)

```
# 	Hospital Course Instrument table 1 HRS_reversal_new
```{r,include=FALSE,echo=FALSE,warning=FALSE,message=FALSE}
hospitalization_course_variables<- c(
  "total_albumin_post_terli",
  "total_prbc_post_terli",
  "gibleed_hosp",
  "gibleed_date",
  "days_to_gibleed",
  "noso_infection",
  "noso_infection_date",
  "days_to_noso_infection",
  "type_noso_infection",
  "other_noso_infection",
  "icu_admit",
  "icu_admit_date",
  "days_to_icu_admit",
  "icu_dc_date",
  "days_to_icu_dc",
  "mv_use",
  "mv_date",
  "days_to_mv",
  "mv_extubation_date",
  "days_to_mv_extubation",
  "norepi_post_terli",
  "norepi_post_terli_date",
  "days_to_norepi_post_terli",
  "norepi_post_terli_dc_date",
  "days_norepi_post_terli",
  "dc_date",
  "days_to_discharge",
  # "dc_available_sna",
  "dc_sna",
  # "dc_available_scr",
  "dc_scr",
  # "dc_available_albumin",
  "dc_albumin",
  # "dc_available_tbili",
  "dc_tbili",
  # "dc_available_inr",
  "dc_inr",
  "nsbb_dc",
  "nsbb_dc_dose",
  "dc_diuretics",
  "dc_k_sparing_diuretic",
  "dc_midodrine",
  "dc_midodrine_total",
  "dc_octreotide",
  "dc_octreotide_total",
  "dc_rifaximin",
  "dc_lactulose",
  "dc_sbp_ppx",
  "disposition",
  "lt_eval",
  "lt_eval_date",
  "days_to_lt_eval",
  "lteval_listingstatus",
  "lt_listing_date",
  "days_to_lt_listing",
  "lt_during_hospital",
  "slkt_during_hospital",
  "lt_date",
  "days_to_lt"
)



hospitalization_course_variables <- hospitalization_course_variables[!grepl("_date$", hospitalization_course_variables)]

setdiff(hospitalization_course_variables,names(final_master))


formula_hospitalization_course_variables<- as.formula(paste("~", paste(hospitalization_course_variables, collapse = " + "), "| HRS_reversal_new"))

cat_hospitalization_course_variables <- c(
  "slkt_during_hospital", "lt_during_hospital", "lteval_listingstatus", "lt_eval", 
  "dc_sbp_ppx", "dc_lactulose", "dc_rifaximin", "dc_midodrine", 
  "dc_k_sparing_diuretic", "dc_diuretics", "nsbb_dc", "norepi_post_terli", 
  "mv_use", "icu_admit", "type_noso_infection", "noso_infection", 
  "gibleed_hosp","dc_octreotide","disposition"
)
final_master$dc_tbili <- as.numeric(str_extract(final_master$dc_tbili, "\\d+\\.?\\d*"))

cat_hospitalization_course_variables <- unique(cat_hospitalization_course_variables)
hospitalization_course_variables <- unique(hospitalization_course_variables)
num_hospitalization_course_variables <- setdiff(hospitalization_course_variables,cat_hospitalization_course_variables)


final_master <- final_master %>% mutate_at(cat_hospitalization_course_variables,as.factor)
```


# hospitalization_course HRS_reversal_new
```{r,include=FALSE}


create_table_one(
  all_vars = hospitalization_course_variables,
  cat_vars = cat_hospitalization_course_variables,
  data     = final_master,
  strata   = "HRS_reversal_new",
  output   = "/Users/to909/Desktop/Tables/table_hospitalization_0508_HRS_reversal_new.csv"
)


```

# hospitalization_course hrs_responders
```{r,include=FALSE}


create_table_one(
  all_vars = hospitalization_course_variables,
  cat_vars = cat_hospitalization_course_variables,
  data     = final_master,
  strata   = "hrs_responders",
  output   = "/Users/to909/Desktop/Tables/table_hospitalization_0508_hrs_responders.csv"
)


```

# hospitalization_course hrs_responders_cat_2
```{r,include=FALSE}


create_table_one(
  all_vars = hospitalization_course_variables,
  cat_vars = cat_hospitalization_course_variables,
  data     = final_master,
  strata   = "hrs_responders_cat_2",
  output   = "/Users/to909/Desktop/Tables/table_hospitalization_0508_hrs_responders_cat_2.csv"
)


```

# hospitalization_course time_to_death_status_90days
```{r,include=FALSE}


create_table_one(
  all_vars = hospitalization_course_variables,
  cat_vars = cat_hospitalization_course_variables,
  data     = final_master,
  strata   = "time_to_death_status_90days",
  output   = "/Users/to909/Desktop/Tables/table_hospitalization_0508_time_to_death_status_90days.csv"
)


```

# hospitalization_course HRS_criteria_3
```{r,include=FALSE}


create_table_one(
  all_vars = hospitalization_course_variables,
  cat_vars = cat_hospitalization_course_variables,
  data     = final_master,
  strata   = "HRS_criteria_3",
  output   = "/Users/to909/Desktop/Tables/table_hospitalization_0508_HRS_criteria_3.csv"
)


```



# 	HRS Clinical  Course Instrument 
```{r,include=FALSE,echo=FALSE,warning=FALSE,message=FALSE}
hrs_clinical_course_variables<- c(
  "scr_day1_post_terli", "scr_day2_post_terli", "scr_day3_post_terli", "scr_day4_post_terli",
  "scr_day5_post_terli", "scr_day6_post_terli", "scr_day7_post_terli", "scr_day8_post_terli",
  "scr_day9_post_terli", "scr_day10_post_terli", "scr_day11_post_terli", "scr_day12_post_terli",
  "scr_day13_post_terli", "scr_day14_post_terli", "HRS_reversal_new", "days_to_hrsreversal",
  "hrsrecovery", "days_to_hrsrecovery", "recurrentaki", "recurrentaki_number",
  "days_to_recurrentaki", "recurrentaki_akietiology", "retreatment_terli", "nadirhospit_scr",
  "days_to_nadirhospit_scr", "peakhospit_scr", "days_to_peakhospitscr", "rrt", "days_to_rrt",
  "rrt_modality", "rrt_continuous", "days_to_rrt_continuous", "hd_discharge",
  "rrt_indication___1",
  "rrt_indication___2",
  "rrt_indication___3",
  "rrt_indication___4",
  "rrt_indication___5",
  "rrt_indication___6",
  "rrt_indication___7",
  "rrt_indication_other"
  
)


# Vector of numerical variables
num_hrs_clinical_course_variables<- c(
  "scr_day1_post_terli", "scr_day2_post_terli", "scr_day3_post_terli", "scr_day4_post_terli",
  "scr_day5_post_terli", "scr_day6_post_terli", "scr_day7_post_terli", "scr_day8_post_terli",
  "scr_day9_post_terli", "scr_day10_post_terli", "scr_day11_post_terli", "scr_day12_post_terli",
  "scr_day13_post_terli", "scr_day14_post_terli", "days_to_hrsreversal", "days_to_hrsrecovery",
   "recurrentaki_number", "days_to_recurrentaki", "nadirhospit_scr",
  "peakhospit_scr", "days_to_peakhospitscr", "days_to_rrt"
)

cat_hrs_clinical_course_variables <- c(
  "HRS_reversal_new",
  "hrsrecovery", "recurrentaki_akietiology", "retreatment_terli", "rrt",
  "rrt_modality", "rrt_continuous", "hd_discharge","recurrentaki",
    "rrt_indication___1",
  "rrt_indication___2",
  "rrt_indication___3",
  "rrt_indication___4",
  "rrt_indication___5",
  "rrt_indication___6",
  "rrt_indication___7",
  "rrt_indication_other"
)



final_master <- final_master %>% mutate_at(num_hrs_clinical_course_variables,as.numeric)


final_master <- final_master %>% mutate_at(cat_hrs_clinical_course_variables,as.factor)


```
# HRS_reversal_new
```{r,include=FALSE}
create_table_one(
  all_vars = hrs_clinical_course_variables,
  cat_vars = cat_hrs_clinical_course_variables,
  data     = final_master,
  strata   = "HRS_reversal_new",
  output   = "/Users/to909/Desktop/Tables/table_hrs_clinical_0508_HRS_reversal_new.csv"
)
```

# hrs_responders
```{r,include=FALSE}
create_table_one(
  all_vars = hrs_clinical_course_variables,
  cat_vars = cat_hrs_clinical_course_variables,
  data     = final_master,
  strata   = "hrs_responders",
  output   = "/Users/to909/Desktop/Tables/table_hrs_clinical_0508_hrs_responders.csv"
)
```

# hrs_responders_cat_2
```{r,include=FALSE}
create_table_one(
  all_vars = hrs_clinical_course_variables,
  cat_vars = cat_hrs_clinical_course_variables,
  data     = final_master,
  strata   = "hrs_responders_cat_2",
  output   = "/Users/to909/Desktop/Tables/table_hrs_clinical_0508_hrs_responders_cat_2.csv"
)
```

# HRS_criteria_3
```{r,include=FALSE}
create_table_one(
  all_vars = hrs_clinical_course_variables,
  cat_vars = cat_hrs_clinical_course_variables,
  data     = final_master,
  strata   = "HRS_criteria_3",
  output   = "/Users/to909/Desktop/Tables/table_hrs_clinical_0508_HRS_criteria_3.csv"
)
```




# time_to_death_status_90days
```{r,include=FALSE}
create_table_one(
  all_vars = hrs_clinical_course_variables,
  cat_vars = cat_hrs_clinical_course_variables,
  data     = final_master,
  strata   = "time_to_death_status_90days",
  output   = "/Users/to909/Desktop/Tables/table_hrs_clinical_0508_time_to_death_status_90days.csv"
)
```

```{r,echo=FALSE,message=FALSE,warning=FALSE}
# AE HRS_reversal_new
# ae_test <- final_master%>% drop_na(Discont_Day)  %>%
#   rowwise() %>%  # Ensure row-wise operations
#   mutate(
#     last_scr = get(paste0("scr_terli_day", Discont_Day)),
# 
#     discont_reason_terli = get(paste0("discont_reason_terli_day", Discont_Day)),
#     terli_ae_abdpain = get(paste0("terli_ae_abdpain_day", Discont_Day)),
#     terli_ae_nausea = get(paste0("terli_ae_nausea_day", Discont_Day)),
#     terli_ae_diarrhea = get(paste0("terli_ae_diarrhea_day", Discont_Day)),
#     terli_ae_volover = get(paste0("terli_ae_volover_day", Discont_Day)),
#     terli_ae_brady = get(paste0("terli_ae_brady_day", Discont_Day)),
#     terli_other = get(paste0("terli_other_day", Discont_Day))
#   ) %>%
#   ungroup() %>%  # Ungroup after row-wise operation
#   select(
#     subjectid,
#     last_scr,
#     Discont_Day,
#     discont_reason_terli,
#     terli_ae_abdpain,
#     terli_ae_nausea,
#     terli_ae_diarrhea,
#     terli_ae_volover,
#     terli_ae_brady,
#     terli_other
#   ) %>% mutate(terli_7 =if_else(discont_reason_terli==7,1,0),
#                terli_8 =if_else(discont_reason_terli==8,1,0))
# 

# ae_test <- ae_test %>% merge(final_master %>% select(subjectid,HRS_reversal_new,hrs_responders),by="subjectid",all.x = T)

# ae_test <- ae_test %>% merge(final_master %>% select(subjectid,HRS_reversal_new,hrs_responders,dosechange_days),by="subjectid",all.x = T)

# table1(~as.factor(terli_ae_abdpain)+
#     as.factor(terli_ae_nausea)+
#     as.factor(terli_ae_diarrhea)+
#     as.factor(terli_ae_volover)+
#     as.factor(terli_ae_brady)+
#     as.factor(terli_7)+
#      as.factor(terli_8)|HRS_reversal_new,ae_test)

```




# numerical_vars HRS_reversal_new
```{r}
numerical_vars_formula <- as.formula(paste("~", paste(numerical_vars, collapse = "+"),"|HRS_reversal_new"))
table1(numerical_vars_formula,data = final_master)
```
# num_hrs_clinical_course_variables HRS_reversal_new
```{r}
num_hrs_clinical_course_variables_formula <- as.formula(paste("~", paste(num_hrs_clinical_course_variables, collapse = "+"),"|HRS_reversal_new"))
table1(num_hrs_clinical_course_variables_formula,data = final_master)
```
# num_hospitalization_course_variables HRS_reversal_new
```{r}
num_hospitalization_course_variables_formula <- as.formula(paste("~", paste(num_hrs_clinical_course_variables, collapse = "+"),"|HRS_reversal_new"))
table1(num_hospitalization_course_variables_formula,data = final_master)
```
# num_followup_variables HRS_reversal_new
```{r}
num_followup_variables_formula <- as.formula(paste("~", paste(num_followup_variables, collapse = "+"),"|HRS_reversal_new"))
table1(num_followup_variables_formula,data = final_master)
```


# numerical_vars hrs_responders
```{r}
numerical_vars_formula <- as.formula(paste("~", paste(numerical_vars, collapse = "+"),"|hrs_responders"))
table1(numerical_vars_formula,data = final_master %>% drop_na(hrs_responders))
```
# num_hrs_clinical_course_variables hrs_responders
```{r}
num_hrs_clinical_course_variables_formula <- as.formula(paste("~", paste(num_hrs_clinical_course_variables, collapse = "+"),"|hrs_responders"))
table1(num_hrs_clinical_course_variables_formula,data = final_master%>% drop_na(hrs_responders))
```
# num_hospitalization_course_variables hrs_responders
```{r}
num_hospitalization_course_variables_formula <- as.formula(paste("~", paste(num_hrs_clinical_course_variables, collapse = "+"),"|hrs_responders"))
table1(num_hospitalization_course_variables_formula,data = final_master%>% drop_na(hrs_responders))
```
# num_followup_variables hrs_responders
```{r}
num_followup_variables_formula <- as.formula(paste("~", paste(num_followup_variables, collapse = "+"),"|hrs_responders"))
table1(num_followup_variables_formula,data = final_master%>% drop_na(hrs_responders))
```





# HRS_reversal_new KM 
```{r echo=FALSE, warning=FALSE, r,message=FALSE}

####################### Subgroup
final_master <- final_master %>% drop_na(HRS_reversal_new,hrs_responders)


final_master$time_to_death_status_90days <-
  as.integer(as.character(final_master$time_to_death_status_90days))

fit_90days_death<- survfit(Surv(time_to_death_90days,time_to_death_status_90days) ~ HRS_reversal_new, data = final_master )


result_90days_death<- ggsurvplot(
  fit_90days_death,                     # survfit object with calculated statistics.
  data = final_master,  # data used to fit survival curves.
  surv.scale = "percent",
  # legend.title = "Etiology of AKI", # legend title
  # legend.labs = c("Prerenal","HRS-AKI","ATN"), # legend labels
  # palette = c("#00ABFD","#7CAE00","#F8766D"),
  pval = T,             # show p-value of log-rank test.
  pval.coord = c(75, 1),# pvalue  position
  pval.size = 4, # pvalue size
  conf.int = FALSE,         # show confidence intervals for
  xlim = c(0,90),  # present narrower X axis, but not affect survival estimates.
  xlab = "Time (days)", # Xlabel.
  break.time.by = 30,     # break X axis in time intervals by 500.
  # ggtheme = theme_minimal(), # customize plot and risk table with a theme.
  tables.theme = theme_cleantable(),
  risk.table = TRUE,       # show risk table.
  risk.table.y.text.col = T, # colour risk table text annotations.
  risk.table.y.text = T, # show bars instead of names in text annotations
  risk.table.fontsize= 4,
  # in legend of risk table
)

result_90days_death$table <- result_90days_death$table + theme(axis.line = element_blank()) + ggtitle("Number of participants entering intervals")
#result_90days_death$plot <- result_90days_death$plot + labs(title = "Survival Curves")
result_90days_death
```



# hrs_responders KM
```{r,message=FALSE,warning=FALSE,echo=FALSE}

####################### Subgroup


fit_90days_death<- survfit(Surv(time_to_death_90days,time_to_death_status_90days) ~ hrs_responders, data = final_master )


##### Prerenal : blue
##### HRS: green
##### ATN: red


result_90days_death<- ggsurvplot(
  fit_90days_death,                     # survfit object with calculated statistics.
  data = final_master,  # data used to fit survival curves.
  surv.scale = "percent",
  # legend.title = "Etiology of AKI", # legend title
  # legend.labs = c("Prerenal","HRS-AKI","ATN"), # legend labels
  # palette = c("#00ABFD","#7CAE00","#F8766D"),
  pval = T,             # show p-value of log-rank test.
  pval.coord = c(75, 1),# pvalue  position
  pval.size = 4, # pvalue size
  conf.int = FALSE,         # show confidence intervals for
  xlim = c(0,90),  # present narrower X axis, but not affect survival estimates.
  xlab = "Time (days)", # Xlabel.
  break.time.by = 30,     # break X axis in time intervals by 500.
  # ggtheme = theme_minimal(), # customize plot and risk table with a theme.
  tables.theme = theme_cleantable(),
  risk.table = TRUE,       # show risk table.
  risk.table.y.text.col = T, # colour risk table text annotations.
  risk.table.y.text = T, # show bars instead of names in text annotations
  risk.table.fontsize= 4,
  # in legend of risk table
)

result_90days_death$table <- result_90days_death$table + theme(axis.line = element_blank()) + ggtitle("Number of participants entering intervals")
#result_90days_death$plot <- result_90days_death$plot + labs(title = "Survival Curves")
result_90days_death
```
# hrs_responders_cat_2 KM
```{r,message=FALSE,warning=FALSE,echo=FALSE}

####################### Subgroup


fit_90days_death<- survfit(Surv(time_to_death_90days,time_to_death_status_90days) ~ hrs_responders_cat_2, data = final_master )


##### Prerenal : blue
##### HRS: green
##### ATN: red


result_90days_death<- ggsurvplot(
  fit_90days_death,                     # survfit object with calculated statistics.
  data = final_master,  # data used to fit survival curves.
  surv.scale = "percent",
  # legend.title = "Etiology of AKI", # legend title
  # legend.labs = c("Prerenal","HRS-AKI","ATN"), # legend labels
  # palette = c("#00ABFD","#7CAE00","#F8766D"),
  pval = T,             # show p-value of log-rank test.
  pval.coord = c(75, 1),# pvalue  position
  pval.size = 4, # pvalue size
  conf.int = FALSE,         # show confidence intervals for
  xlim = c(0,90),  # present narrower X axis, but not affect survival estimates.
  xlab = "Time (days)", # Xlabel.
  break.time.by = 30,     # break X axis in time intervals by 500.
  # ggtheme = theme_minimal(), # customize plot and risk table with a theme.
  tables.theme = theme_cleantable(),
  risk.table = TRUE,       # show risk table.
  risk.table.y.text.col = T, # colour risk table text annotations.
  risk.table.y.text = T, # show bars instead of names in text annotations
  risk.table.fontsize= 4,
  # in legend of risk table
)

result_90days_death$table <- result_90days_death$table + theme(axis.line = element_blank()) + ggtitle("Number of participants entering intervals")
#result_90days_death$plot <- result_90days_death$plot + labs(title = "Survival Curves")
result_90days_death
```



# ae by HRS_Criteria 
```{r,echo=FALSE,message=FALSE,warning=FALSE}


ae_vars <- c(
  "any_ae",
  "terli_ae_abdpain",
  "terli_ae_nausea",
  "terli_ae_diarrhea",
  "terli_ae_volover",
  "terli_ae_brady",
  "terli_7",
  "terli_8",
  "terli_ae_respfail"
)

# table1(~as.factor(terli_ae_abdpain)+
#     as.factor(terli_ae_nausea)+
#     as.factor(terli_ae_diarrhea)+
#     as.factor(terli_ae_volover)+
#     as.factor(terli_ae_brady)+
#     as.factor(terli_7)+
#      as.factor(terli_8)+
#       as.factor(terli_ae_respfail)|HRS_Criteria,final_master %>% drop_na(HRS_Criteria))

T1_ae <- tableone::CreateTableOne(
    vars       = ae_vars,
    strata     = "HRS_Criteria",        # variable to stratify by
    data       = final_master,
    factorVars = ae_vars,      # specify which variables are factors
    addOverall = TRUE,
    includeNA  = FALSE
  )

  # 2) Print TableOne object and convert to data frame
       print1 <- print(
      T1_ae,
      showAllLevels = T,
      missing       = TRUE,
      quote         = FALSE,
      noSpaces      = TRUE,
      printToggle   = FALSE,
      exact = ae_vars[!ae_vars %in% c("terli_ae_respfail","any_ae") ]
    )
 write.csv(print1, file = "/Users/to909/Desktop/Tables/ae by HRS_Criteria.csv")
```

# ae by HRS_Criteria 
```{r,echo=FALSE,message=FALSE,warning=FALSE}


ae_vars <- c(
  "any_ae",
  "terli_ae_abdpain",
  "terli_ae_nausea",
  "terli_ae_diarrhea",
  "terli_ae_volover",
  "terli_ae_brady",
  "terli_7",
  "terli_8",
  "terli_ae_respfail"
)

# table1(~as.factor(terli_ae_abdpain)+
#     as.factor(terli_ae_nausea)+
#     as.factor(terli_ae_diarrhea)+
#     as.factor(terli_ae_volover)+
#     as.factor(terli_ae_brady)+
#     as.factor(terli_7)+
#      as.factor(terli_8)+
#       as.factor(terli_ae_respfail)|HRS_Criteria,final_master %>% drop_na(HRS_Criteria))

T1_ae <- tableone::CreateTableOne(
    vars       = ae_vars,
    strata     = "HRS_criteria_3",        # variable to stratify by
    data       = final_master,
    factorVars = ae_vars,      # specify which variables are factors
    addOverall = TRUE,
    includeNA  = FALSE
  )

  # 2) Print TableOne object and convert to data frame
       print1 <- print(
      T1_ae,
      showAllLevels = T,
      missing       = TRUE,
      quote         = FALSE,
      noSpaces      = TRUE,
      printToggle   = FALSE,
      exact = ae_vars[!ae_vars %in% c("terli_ae_respfail","any_ae") ]
    )
 write.csv(print1, file = "/Users/to909/Desktop/Tables/ae by HRS_criteria_3.csv")
 
 
```


# ae by terli_route_day0 missing terli_route_day0 
```{r,echo=FALSE,message=FALSE,warning=FALSE}

# table1(~as.factor(terli_ae_abdpain)+
#     as.factor(terli_ae_nausea)+
#     as.factor(terli_ae_diarrhea)+
#     as.factor(terli_ae_volover)+
#     as.factor(terli_ae_brady)+
#     as.factor(terli_7)+
#      as.factor(terli_8)+
#       as.factor(terli_ae_respfail)|terli_route_day0 ,final_master )



 T1_ae <- tableone::CreateTableOne(
    vars       = ae_vars,
    strata     = "terli_route_day0",        # variable to stratify by
    data       = final_master,
    factorVars = ae_vars,      # specify which variables are factors
    addOverall = TRUE,
    includeNA  = FALSE
  )

  # 2) Print TableOne object and convert to data frame
    print1 <- print(
      T1_ae,
      showAllLevels = T,
      missing       = TRUE,
      quote         = FALSE,
      noSpaces      = TRUE,
      printToggle   = FALSE,
      exact = ae_vars
    )
  write.csv(print1, file = "/Users/to909/Desktop/Tables/ae by terli_route_day0.csv")

```



# ae by  meld_35
```{r,echo=FALSE,message=FALSE,warning=FALSE}

final_master <- final_master %>% mutate(meld_35=if_else(admit_meld_3_raw>=35,">=35","<35"))


 T1_ae <- tableone::CreateTableOne(
    vars       = ae_vars,
    strata     = "meld_35",        # variable to stratify by
    data       = final_master,
    factorVars = ae_vars,      # specify which variables are factors
    addOverall = TRUE,
    includeNA  = FALSE
  )

  # 2) Print TableOne object and convert to data frame
    print1 <- print(
      T1_ae,
      showAllLevels = T,
      missing       = TRUE,
      quote         = FALSE,
      noSpaces      = TRUE,
      printToggle   = FALSE,
      exact = ae_vars
    )
  write.csv(print1, file = "/Users/to909/Desktop/Tables/ae by meld_35.csv")

```



# ae by  criteria_2
```{r,echo=FALSE,message=FALSE,warning=FALSE}

final_master %>% mutate(criteria_2=if_else(admit_meld_3_raw>=35,">=35","<35"))


 T1_ae <- tableone::CreateTableOne(
    vars       = ae_vars,
    strata     = "criteria_2",        # variable to stratify by
    data       = final_master,
    factorVars = ae_vars,      # specify which variables are factors
    addOverall = TRUE,
    includeNA  = FALSE
  )

  # 2) Print TableOne object and convert to data frame
    print1 <- print(
      T1_ae,
      showAllLevels = T,
      missing       = TRUE,
      quote         = FALSE,
      noSpaces      = TRUE,
      printToggle   = FALSE,
      exact = ae_vars
    )
  write.csv(print1, file = "/Users/to909/Desktop/Tables/ae by criteria_2.csv")

```






# scr_category by HRS_reversal_new
```{r,include=T,echo=FALSE,message=FALSE,warning=FALSE}
a <- final_master %>%
  mutate(scr_category = cut(scr_terli_day0,
                            breaks = c(-Inf, 1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5, Inf),
                            labels = c("<1.5", "1.5-2", "2-2.5", "2.5-3", "3-3.5",
                                       "3.5-4", "4-4.5", "4.5-5", ">5"),
                            right = FALSE))


gmodels::CrossTable(a$scr_category,a$HRS_reversal_new)

```


# scr_category by hrs_responders_cat_2
```{r,include=T,echo=FALSE,message=FALSE,warning=FALSE}
a <- final_master %>%
  mutate(scr_category = cut(scr_terli_day0,
                            breaks = c(-Inf, 1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5, Inf),
                            labels = c("<1.5", "1.5-2", "2-2.5", "2.5-3", "3-3.5",
                                       "3.5-4", "4-4.5", "4.5-5", ">5"),
                            right = FALSE))


gmodels::CrossTable(a$scr_category,a$hrs_responders_cat_2)

```


# quintiles of admit_meld_3_raw by HRS_reversal_new
```{r,include=T,echo=FALSE,message=FALSE,warning=FALSE}
a <- final_master %>% drop_na(admit_meld_3_raw) 
a$admit_meld_3_raw_quintile <- cut(
  a$admit_meld_3_raw,
  breaks = quantile(a$admit_meld_3_raw, probs = seq(0, 1, 0.2), na.rm = TRUE),
  include.lowest = TRUE,
  labels = FALSE
)

gmodels::CrossTable(a$admit_meld_3_raw_quintile,a$HRS_reversal_new)

```


# quintiles of tbili_admit by HRS_reversal_new
```{r,include=T,echo=FALSE,message=FALSE,warning=FALSE}

a$tbili_admit_quintile <- cut(
  a$tbili_admit,
  breaks = quantile(a$tbili_admit, probs = seq(0, 1, 0.2), na.rm = TRUE),
  include.lowest = TRUE,
  labels = FALSE
)

gmodels::CrossTable(a$tbili_admit_quintile,a$HRS_reversal_new)
# write.xlsx(as.data.frame(final_master),"/Users/to909/Desktop/final_master_check_0508.xlsx",showNA = F,row.names= F)
```





# 1 Unviariate Logistic regression:  time_to_death_status_90days
```{r,echo=FALSE,warning=FALSE,message=F,include=FALSE}

final_master %>% 
  select(HRS_reversal_new,age,race_2,hispanic,admit_meld_3,listed_transplant,time_to_death_status_90days) %>%
  tbl_uvregression(
    method = glm,
    method.args = list(family = binomial),
    y = time_to_death_status_90days,
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  ) %>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```


# 2 Multivariate Logistic regression:time_to_death_status_90days  
```{r,echo=FALSE,warning=FALSE,message=F,include=FALSE}
glm( time_to_death_status_90days ~HRS_reversal_new+ age+race_2+hispanic+admit_meld_3+listed_transplant,family = binomial, data = final_master) %>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```




# 3 Unviariate Logistic regression:  time_to_death_status_90days
```{r,echo=FALSE,warning=FALSE,message=F,include=FALSE}

final_master %>% 
  select(hrs_responders_cat_2,age,race_2,hispanic,admit_meld_3,listed_transplant,time_to_death_status_90days) %>%
  tbl_uvregression(
    method = glm,
    method.args = list(family = binomial),
    y = time_to_death_status_90days,
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  ) %>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```


# 4 Multivariate Logistic regression:time_to_death_status_90days  
```{r,echo=FALSE,warning=FALSE,message=F,include=FALSE}
glm( time_to_death_status_90days ~hrs_responders_cat_2+ age+race_2+hispanic+admit_meld_3+listed_transplant,family = binomial, data = final_master) %>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```







# 5 Unviariate Logistic regression:  transplant_outcome
```{r,echo=FALSE,warning=FALSE,message=F,include=FALSE}

final_master %>% 
  select(HRS_reversal_new,age,race_2,hispanic,admit_meld_3,transplant_outcome) %>%
  tbl_uvregression(
    method = glm,
    method.args = list(family = binomial),
    y = transplant_outcome,
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  ) %>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```


# 6 Multivariate Logistic regression:transplant_outcome
```{r,echo=FALSE,warning=FALSE,message=F,include=FALSE}
glm( transplant_outcome ~HRS_reversal_new+ age+race_2+hispanic+admit_meld_3,family = binomial, data = final_master) %>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```




# 7 Unviariate Logistic regression:  transplant_outcome
```{r,echo=FALSE,warning=FALSE,message=F,include=FALSE}

final_master %>% 
  select(hrs_responders_cat_2,age,race_2,hispanic,admit_meld_3,transplant_outcome) %>%
  tbl_uvregression(
    method = glm,
    method.args = list(family = binomial),
    y = transplant_outcome,
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  ) %>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```


# 8 Multivariate Logistic regression:transplant_outcome
```{r,echo=FALSE,warning=FALSE,message=F,include=FALSE}
glm( transplant_outcome ~hrs_responders_cat_2+ age+race_2+hispanic+admit_meld_3,family = binomial, data = final_master) %>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```






# 9.1 Unviariate cmp:  time_to_death_status_90days_cmp failcode=1
```{r,echo=FALSE,warning=FALSE,message=F}

final_master %>% 
  select(hrs_responders_cat_2,age,race_2,hispanic,admit_meld_3,time_to_death_90days_cmp,time_to_death_status_90days_cmp) %>%
  tbl_uvregression(
    method = tidycmprsk::crr,
    method.args = list(failcode=1,cencode=0),
    y = Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp),
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  )

```
# 9.2 Unviariate cmp:  time_to_death_status_90days_cmp failcode=2
```{r,echo=FALSE,warning=FALSE,message=F}



final_master %>% 
  select(hrs_responders_cat_2, age, race_2, hispanic, admit_meld_3,
         time_to_death_90days_cmp, time_to_death_status_90days_cmp) %>%
  tbl_uvregression(
    method = tidycmprsk::crr,
    method.args = list(failcode = 2, cencode = 0),
    y = Surv(time_to_death_90days_cmp, time_to_death_status_90days_cmp),
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  ) %>%
  bold_p(0.05) %>%
  bold_labels()

```
# 10.1 Multiviariate cmp:  time_to_death_status_90days_cmp failcode=1
```{r,echo=FALSE,warning=FALSE,message=F}
tidycmprsk::crr(Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp) ~hrs_responders_cat_2+age+race_2+hispanic+admit_meld_3,failcode=1,cencode=0, data = final_master) %>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```


# 10.2 Multiviariate cmp:  time_to_death_status_90days_cmp failcode=2
```{r,echo=FALSE,warning=FALSE,message=F}
tidycmprsk::crr(Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp) ~hrs_responders_cat_2+age+race_2+hispanic+admit_meld_3,failcode=2,cencode=0, data = final_master) %>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```

# 11.1 Unviariate cmp:  time_to_death_status_90days_cmp failcode=1
```{r,echo=FALSE,warning=FALSE,message=F}

final_master %>% 
  select(HRS_reversal_new,age,race_2,hispanic,admit_meld_3,time_to_death_90days_cmp,time_to_death_status_90days_cmp) %>%
  tbl_uvregression(
    method = tidycmprsk::crr,
    method.args = list(failcode=1,cencode=0),
    y = Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp),
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  )

```

# 11.2 Unviariate cmp:  time_to_death_status_90days_cmp failcode=2
```{r,echo=FALSE,warning=FALSE,message=F}

final_master %>% 
  select(HRS_reversal_new,age,race_2,hispanic,admit_meld_3,time_to_death_90days_cmp,time_to_death_status_90days_cmp) %>%
  tbl_uvregression(
    method = tidycmprsk::crr,
    method.args = list(failcode=2,cencode=0),
    y = Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp),
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  )

```

# 12.1 Multiviariate cmp:  time_to_death_status_90days_cmp failcode=1
```{r,echo=FALSE,warning=FALSE,message=F}
tidycmprsk::crr(Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp) ~HRS_reversal_new+age+race_2+hispanic+admit_meld_3,failcode=1,cencode=0, data = final_master) %>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```

# 12.2 Multiviariate cmp:  time_to_death_status_90days_cmp failcode=2
```{r,echo=FALSE,warning=FALSE,message=F}
tidycmprsk::crr(Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp) ~HRS_reversal_new+age+race_2+hispanic+admit_meld_3,failcode=2,cencode=0, data = final_master) %>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```





# 13 Unviariate Logistic regression:  transplant_outcome
```{r,echo=FALSE,warning=FALSE,message=F}

final_master %>% filter(listed_transplant == 1)  %>% 
  select(HRS_reversal_new,age,race_2,hispanic,admit_meld_3,transplant_outcome) %>%
  tbl_uvregression(
    method = glm,
    method.args = list(family = binomial),
    y = transplant_outcome,
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  ) %>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```


# 14 Multivariate Logistic regression:transplant_outcome
```{r,echo=FALSE,warning=FALSE,message=F}
glm( transplant_outcome ~HRS_reversal_new+ age+race_2+hispanic+admit_meld_3,family = binomial, data = final_master %>% filter(listed_transplant == 1) ) %>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```




# 15 Unviariate Logistic regression:  transplant_outcome
```{r,echo=FALSE,warning=FALSE,message=F}

final_master %>% filter(listed_transplant == 1)  %>% 
  select(hrs_responders_cat_2,age,race_2,hispanic,admit_meld_3,transplant_outcome) %>%
  tbl_uvregression(
    method = glm,
    method.args = list(family = binomial),
    y = transplant_outcome,
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  ) %>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```


# 16 Multivariate Logistic regression:transplant_outcome
```{r,echo=FALSE,warning=FALSE,message=F}
glm( transplant_outcome ~hrs_responders_cat_2+ age+race_2+hispanic+admit_meld_3,family = binomial, data = final_master %>% filter(listed_transplant == 1) ) %>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```



# 5 Unviariate Logistic regression:  transplant_outcome listed_transplant
```{r,echo=FALSE,warning=FALSE,message=F}

final_master %>% filter(listed_transplant==1) %>% 
  select(HRS_reversal_new,age,race_2,hispanic,admit_meld_3,transplant_outcome) %>%
  tbl_uvregression(
    method = glm,
    method.args = list(family = binomial),
    y = transplant_outcome,
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  ) %>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```


# 6 Multivariate Logistic regression:transplant_outcome listed_transplant
```{r,echo=FALSE,warning=FALSE,message=F}
glm( transplant_outcome ~HRS_reversal_new+ age+race_2+hispanic+admit_meld_3,family = binomial, data = final_master %>% filter(listed_transplant==1)  ) %>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```




# 7 Unviariate Logistic regression:  transplant_outcome listed_transplant
```{r,echo=FALSE,warning=FALSE,message=F}

final_master %>% filter(listed_transplant==1) %>% 
  select(hrs_responders_cat_2,age,race_2,hispanic,admit_meld_3,transplant_outcome) %>%
  tbl_uvregression(
    method = glm,
    method.args = list(family = binomial),
    y = transplant_outcome,
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  ) %>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```


# 8 Multivariate Logistic regression:transplant_outcome listed_transplant
```{r,echo=FALSE,warning=FALSE,message=F}
glm( transplant_outcome ~hrs_responders_cat_2+ age+race_2+hispanic+admit_meld_3,family = binomial, data = final_master %>% filter(listed_transplant==1) ) %>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```





# 9.1 Unviariate cmp:  time_to_death_status_90days_cmp failcode=1 listed_transplant==1
```{r,echo=FALSE,warning=FALSE,message=F}


final_master_listed <- final_master %>% filter(listed_transplant==1)


final_master_listed %>% 
  select(hrs_responders_cat_2,age,race_2,hispanic,admit_meld_3,time_to_death_90days_cmp,time_to_death_status_90days_cmp) %>%
  tbl_uvregression(
    method = tidycmprsk::crr,
    method.args = list(failcode=1,cencode=0),
    y = Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp),
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  )

```
# 9.2 Unviariate cmp:  time_to_death_status_90days_cmp failcode=2 final_master_listed=1
```{r,echo=FALSE,warning=FALSE,message=F}

final_master_listed %>% 
  select(hrs_responders_cat_2,age,race_2,hispanic,admit_meld_3,time_to_death_90days_cmp,time_to_death_status_90days_cmp) %>%
  tbl_uvregression(
    method = tidycmprsk::crr,
    method.args = list(failcode=2,cencode=0),
    y = Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp),
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  )

```
# 10.1 Multiviariate cmp:  time_to_death_status_90days_cmp failcode=1 final_master_listed=1
```{r,echo=FALSE,warning=FALSE,message=F}
tidycmprsk::crr(Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp) ~hrs_responders_cat_2+age+race_2+hispanic+admit_meld_3,failcode=1,cencode=0, data = final_master_listed) %>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```


# 10.2 Multiviariate cmp:  time_to_death_status_90days_cmp failcode=2 final_master_listed=1
```{r,echo=FALSE,warning=FALSE,message=F}
tidycmprsk::crr(Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp) ~hrs_responders_cat_2+age+race_2+hispanic+admit_meld_3,failcode=2,cencode=0, data = final_master_listed) %>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```

# 11.1 Unviariate cmp:  time_to_death_status_90days_cmp failcode=1 final_master_listed=1
```{r,echo=FALSE,warning=FALSE,message=F}

final_master_listed %>% 
  select(HRS_reversal_new,age,race_2,hispanic,admit_meld_3,time_to_death_90days_cmp,time_to_death_status_90days_cmp) %>%
  tbl_uvregression(
    method = tidycmprsk::crr,
    method.args = list(failcode=1,cencode=0),
    y = Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp),
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  )

```

# 11.2 Unviariate cmp:  time_to_death_status_90days_cmp failcode=2 final_master_listed=1
```{r,echo=FALSE,warning=FALSE,message=F}

final_master_listed %>% 
  select(HRS_reversal_new,age,race_2,hispanic,admit_meld_3,time_to_death_90days_cmp,time_to_death_status_90days_cmp) %>%
  tbl_uvregression(
    method = tidycmprsk::crr,
    method.args = list(failcode=2,cencode=0),
    y = Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp),
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  )

```

# 12.1 Multiviariate cmp:  time_to_death_status_90days_cmp failcode=1 final_master_listed=1
```{r,echo=FALSE,warning=FALSE,message=F}
tidycmprsk::crr(Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp) ~HRS_reversal_new+age+race_2+hispanic+admit_meld_3,failcode=1,cencode=0, data = final_master_listed) %>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```

# 12.2 Multiviariate cmp:  time_to_death_status_90days_cmp failcode=2 final_master_listed=1
```{r,echo=FALSE,warning=FALSE,message=F}
tidycmprsk::crr(Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp) ~HRS_reversal_new+age+race_2+hispanic+admit_meld_3,failcode=2,cencode=0, data = final_master_listed) %>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```




# 16 Unviariate coxph regression: time_to_death_90days
```{r,echo=FALSE,warning=FALSE,message=F}

final_master %>% 
  select(HRS_reversal_new,age,race_2,hispanic,admit_meld_3,listed_transplant,time_to_death_90days,time_to_death_status_90days) %>%
  tbl_uvregression(
    method = coxph,
    y = Surv(time_to_death_90days,time_to_death_status_90days),
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  ) %>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 


final_master %>% filter(time_to_death_90days>=0) %>% 
  select(HRS_reversal_new,age,race_2,hispanic,admit_meld_3,listed_transplant,time_to_death_90days,time_to_death_status_90days) %>%
  tbl_uvregression(
    method = coxph,
    y = Surv(time_to_death_90days,time_to_death_status_90days),
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  ) %>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```


# 17 Multivariate coxph regression: time_to_death_90days
```{r,echo=FALSE,warning=FALSE,message=F}
coxph(Surv(time_to_death_90days, time_to_death_status_90days) ~ 
        HRS_reversal_new + age + race_2 + hispanic + admit_meld_3 + listed_transplant,
      data = final_master) %>%
  tbl_regression(exp = TRUE) %>%
  add_n() %>%
  bold_p(0.05) %>%
  bold_labels()

```




# 18 Unviariate coxph regression: 
```{r,echo=FALSE,warning=FALSE,message=F}

final_master %>% 
  select(hrs_responders_cat_2,age,race_2,hispanic,admit_meld_3,listed_transplant,time_to_death_90days,time_to_death_status_90days) %>%
  tbl_uvregression(
    method = coxph,
   
    y = Surv(time_to_death_90days,time_to_death_status_90days),
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  ) %>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```


# 19 Multivariate coxph regression:
```{r,echo=FALSE,warning=FALSE,message=F}
coxph(Surv(time_to_death_90days, time_to_death_status_90days) ~ 
        hrs_responders_cat_2 + age + race_2 + hispanic + admit_meld_3 + listed_transplant,
      data = final_master) %>%
  tbl_regression(exp = TRUE) %>%
  add_n() %>%
  bold_p(0.05) %>%
  bold_labels()

```







# 20 Unviariate coxph regression:  transplant_outcome
```{r,echo=FALSE,warning=FALSE,message=F}
final_master <- final_master %>% mutate(time_to_transplant_status_90days_1=ifelse(time_to_transplant_status_90days==2,1,0))
final_master %>% 
  select(HRS_reversal_new,age,race_2,hispanic,admit_meld_3,time_to_transplant_90days,time_to_transplant_status_90days_1) %>%
  tbl_uvregression(
    method = coxph,
   
    y = Surv(time_to_transplant_90days,time_to_transplant_status_90days_1),
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  ) %>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```


# 21 Multivariate coxph regression:transplant_outcome
```{r,echo=FALSE,warning=FALSE,message=F}


coxph(Surv(time_to_transplant_90days,time_to_transplant_status_90days_1) ~ 
        HRS_reversal_new+ age+race_2+hispanic+admit_meld_3,
      data = final_master) %>%
  tbl_regression(exp = TRUE) %>%
  add_n() %>%
  bold_p(0.05) %>%
  bold_labels()
```




# 22 Unviariate coxph regression:  transplant_outcome
```{r,echo=FALSE,warning=FALSE,message=F}
final_master %>% 
  select(hrs_responders_cat_2, age, race_2, hispanic, admit_meld_3, 
         time_to_transplant_90days, time_to_transplant_status_90days_1) %>%
  tbl_uvregression(
    method = coxph,
    y = Surv(time_to_transplant_90days, time_to_transplant_status_90days_1),
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  ) %>%
  bold_p(0.05) %>%
  bold_labels()
```


# 23 Multivariate coxph regression:transplant_outcome
```{r,echo=FALSE,warning=FALSE,message=F}


coxph(Surv(time_to_transplant_90days,time_to_transplant_status_90days_1) ~ 
       hrs_responders_cat_2+ age+race_2+hispanic+admit_meld_3,
      data = final_master) %>%
  tbl_regression(exp = TRUE) %>%
  add_n() %>%
  bold_p(0.05) %>%
  bold_labels()

```

# Map 
```{r,echo=FALSE,warning=FALSE,message=F}

# create scr_day
map_days <- grep("^map_terli_day", str_sort(names(final_master)), value = TRUE)


df_long_map <- final_master %>% filter(!is.na(hrs_responders_cat_2)) %>% 
  pivot_longer(
    cols = starts_with("map_terli_day"), 
    names_to = c("temp", "day", "time"),    # we will capture these parts
    names_pattern = "^(map_terli)_day(\\d+)_time(\\d+)$", # regex to split
    values_to = "map"
  ) %>%
  # 2) Convert day/time to numeric so we can sort properly
  mutate(
    day = as.numeric(day),
    time = as.numeric(time)
  ) %>%
  select(-temp)  # 'temp' is just the literal "map_terli", can drop if not needed


df_summary_map <- df_long_map %>%
  group_by(subjectid, day) %>% select(subjectid,hrs_responders_cat_2, day,map)%>%
  filter(day<=3) %>% summarise(map=mean(map,na.rm=T))


df_summary_map <-df_summary_map %>% merge(final_master %>% select(subjectid,hrs_responders_cat_2),all.x = T,by="subjectid")

df_summary_map_wide <- df_summary_map %>%
  pivot_wider(
    id_cols = subjectid,
    names_from = day,
    values_from = map,
    names_prefix = "map_day_"
  )


 

df_summary_map_wide  <-df_summary_map_wide  %>% merge(final_master %>% select(subjectid,hrs_responders_cat_2),all.x = T,by="subjectid")
df_summary_map_wide  <-df_summary_map_wide %>% mutate(map_diff_day3_0=map_day_3-map_day_0,map_diff_day2_0=map_day_2-map_day_0)


###################### 
T1_map<- CreateTableOne(vars = c("map_day_0","map_day_2","map_day_3","map_diff_day3_0","map_diff_day2_0"),strata = "hrs_responders_cat_2",includeNA = F,addOverall = TRUE,data = df_summary_map_wide)
#print table one 
T1_map_csv <- print(T1_map, nonnormal=c("map_day_0","map_day_2","map_day_3","map_diff_day3_0","map_diff_day2_0"),showAllLevels = F ,missing = T,quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
#save 
write.csv(T1_map_csv, file = "/Users/to909/Desktop/Tables/Table_T1_map_diff.csv")


```



# added 1 Unviariate cmp:  time_to_death_status_90days_cmp failcode=1  
```{r,echo=FALSE,warning=FALSE,message=F}

final_master %>% 
  select(hrs_responders_cat_2,age,race_2,hispanic,admit_meld_3,time_to_death_90days_cmp,time_to_death_status_90days_cmp) %>%
  tbl_uvregression(
    method = tidycmprsk::crr,
    method.args = list(failcode=1,cencode=0),
    y = Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp),
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  )

```

# added 1 Multiviariate cmp:  time_to_death_status_90days_cmp failcode=1 
```{r,echo=FALSE,warning=FALSE,message=F}
tidycmprsk::crr(Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp) ~hrs_responders_cat_2+age+race_2+hispanic+admit_meld_3,failcode=1,cencode=0, data = final_master )%>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```



# added 2 Unviariate cmp:  time_to_death_status_90days_cmp failcode=1 HRS_criteria_3 == 1
```{r,echo=FALSE,warning=FALSE,message=F}

final_master %>% filter(HRS_criteria_3 == 1) %>% 
  select(hrs_responders_cat_2,age,race_2,hispanic,admit_meld_3,time_to_death_90days_cmp,time_to_death_status_90days_cmp) %>%
  tbl_uvregression(
    method = tidycmprsk::crr,
    method.args = list(failcode=1,cencode=0),
    y = Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp),
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  )

```

# added 2 Multiviariate cmp:  time_to_death_status_90days_cmp failcode=1  HRS_criteria_3 == 1
```{r,echo=FALSE,warning=FALSE,message=F}
tidycmprsk::crr(Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp) ~hrs_responders_cat_2+age+race_2+hispanic+admit_meld_3,failcode=1,cencode=0, data = final_master %>% filter(HRS_criteria_3 == 1) )%>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```

# added 3 Unviariate cmp:  time_to_death_status_90days_cmp failcode=1 HRS_criteria_3 == 0
```{r,echo=FALSE,warning=FALSE,message=F}

final_master %>% filter(HRS_criteria_3 == 0) %>% 
  select(hrs_responders_cat_2,age,race_2,hispanic, admit_meld_3,time_to_death_90days_cmp,time_to_death_status_90days_cmp) %>%
  tbl_uvregression(
    method = tidycmprsk::crr,
    method.args = list(failcode=1,cencode=0),
    y = Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp),
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  )

```

# added 3 Multiviariate cmp:  time_to_death_status_90days_cmp failcode=1  HRS_criteria_3 == 0
```{r,echo=FALSE,warning=FALSE,message=F}
tidycmprsk::crr(Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp) ~hrs_responders_cat_2+age+race_2+hispanic+admit_meld_3,failcode=1,cencode=0, data = final_master %>% filter(HRS_criteria_3 == 0) )%>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```



# added 4 Unviariate cmp:  time_to_death_status_90days_cmp failcode=2 listed_transplant == 1
```{r,echo=FALSE,warning=FALSE,message=F}

final_master %>% filter(listed_transplant == 1) %>% 
  select(hrs_responders_cat_2,age,race_2,hispanic,admit_meld_3,time_to_death_90days_cmp,time_to_death_status_90days_cmp) %>%
  tbl_uvregression(
    method = tidycmprsk::crr,
    method.args = list(failcode=2,cencode=0),
    y = Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp),
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  )

```

# added 4 Multiviariate cmp:  time_to_death_status_90days_cmp failcode=2  listed_transplant == 1
```{r,echo=FALSE,warning=FALSE,message=F}
tidycmprsk::crr(Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp) ~hrs_responders_cat_2+age+race_2+hispanic+admit_meld_3,failcode=2,cencode=0, data = final_master %>% filter(listed_transplant == 1) )%>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```


# added 5 Unviariate cmp:  time_to_death_status_90days_cmp failcode=2 listed_transplant == 0
```{r,echo=FALSE,warning=FALSE,message=F}

final_master %>% filter(listed_transplant == 0) %>% 
  select(hrs_responders_cat_2,age,race_2,hispanic,admit_meld_3,time_to_death_90days_cmp,time_to_death_status_90days_cmp) %>%
  tbl_uvregression(
    method = tidycmprsk::crr,
    method.args = list(failcode=2,cencode=0),
    y = Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp),
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  )

```

# added 5 Multiviariate cmp:  time_to_death_status_90days_cmp failcode=2  listed_transplant == 0
```{r,echo=FALSE,warning=FALSE,message=F}
tidycmprsk::crr(Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp) ~hrs_responders_cat_2+age+race_2+hispanic+admit_meld_3,failcode=2,cencode=0, data = final_master %>% filter(listed_transplant == 0) )%>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```






# added 1.1 Multiviariate cmp:  time_to_death_status_90days_cmp failcode=1 
```{r,echo=FALSE,warning=FALSE,message=F}
tidycmprsk::crr(Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp) ~HRS_reversal_new+age+race_2+hispanic+admit_meld_3,failcode=1,cencode=0, data = final_master )%>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```



# added 2.1 Unviariate cmp:  time_to_death_status_90days_cmp failcode=1 HRS_criteria_3 == 1
```{r,echo=FALSE,warning=FALSE,message=F}

final_master %>% filter(HRS_criteria_3 == 1) %>% 
  select(HRS_reversal_new,age,race_2,hispanic,admit_meld_3,time_to_death_90days_cmp,time_to_death_status_90days_cmp) %>%
  tbl_uvregression(
    method = tidycmprsk::crr,
    method.args = list(failcode=1,cencode=0),
    y = Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp),
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  )

```

# added 2.1 Multiviariate cmp:  time_to_death_status_90days_cmp failcode=1  HRS_criteria_3 == 1
```{r,echo=FALSE,warning=FALSE,message=F}
tidycmprsk::crr(Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp) ~HRS_reversal_new+age+race_2+hispanic+admit_meld_3,failcode=1,cencode=0, data = final_master %>% filter(HRS_criteria_3 == 1) )%>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```

# added 3.1 Unviariate cmp:  time_to_death_status_90days_cmp failcode=1 HRS_criteria_3 == 0
```{r,echo=FALSE,warning=FALSE,message=F}

final_master %>% filter(HRS_criteria_3 == 0) %>% 
  select(HRS_reversal_new,age,race_2,hispanic, admit_meld_3,time_to_death_90days_cmp,time_to_death_status_90days_cmp) %>%
  tbl_uvregression(
    method = tidycmprsk::crr,
    method.args = list(failcode=1,cencode=0),
    y = Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp),
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  )

```

# added 3.1 Multiviariate cmp:  time_to_death_status_90days_cmp failcode=1  HRS_criteria_3 == 0
```{r,echo=FALSE,warning=FALSE,message=F}
tidycmprsk::crr(Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp) ~HRS_reversal_new+age+race_2+hispanic+admit_meld_3,failcode=1,cencode=0, data = final_master %>% filter(HRS_criteria_3 == 0) )%>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```



# added 4.1 Unviariate cmp:  time_to_death_status_90days_cmp failcode=2 listed_transplant == 1
```{r,echo=FALSE,warning=FALSE,message=F}

final_master %>% filter(listed_transplant == 1) %>% 
  select(HRS_reversal_new,age,race_2,hispanic,admit_meld_3,time_to_death_90days_cmp,time_to_death_status_90days_cmp) %>%
  tbl_uvregression(
    method = tidycmprsk::crr,
    method.args = list(failcode=2,cencode=0),
    y = Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp),
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  )

```

# added 4.1 Multiviariate cmp:  time_to_death_status_90days_cmp failcode=2  listed_transplant == 1
```{r,echo=FALSE,warning=FALSE,message=F}
tidycmprsk::crr(Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp) ~HRS_reversal_new+age+race_2+hispanic+admit_meld_3,failcode=2,cencode=0, data = final_master %>% filter(listed_transplant == 1) )%>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```


# added 5.1 Unviariate cmp:  time_to_death_status_90days_cmp failcode=2 listed_transplant == 0
```{r,echo=FALSE,warning=FALSE,message=F}

final_master %>% filter(listed_transplant == 0) %>% 
  select(HRS_reversal_new,age,race_2,hispanic,admit_meld_3,time_to_death_90days_cmp,time_to_death_status_90days_cmp) %>%
  tbl_uvregression(
    method = tidycmprsk::crr,
    method.args = list(failcode=2,cencode=0),
    y = Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp),
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    exponentiate = TRUE
  )

```

# added 5.1 Multiviariate cmp:  time_to_death_status_90days_cmp failcode=2  listed_transplant == 0
```{r,echo=FALSE,warning=FALSE,message=F}
tidycmprsk::crr(Surv(time_to_death_90days_cmp,time_to_death_status_90days_cmp) ~HRS_reversal_new+age+race_2+hispanic+admit_meld_3,failcode=2,cencode=0, data = final_master %>% filter(listed_transplant == 0) )%>% tbl_regression(exp = TRUE) %>% add_n()%>%
  bold_p(0.05) %>%        # bold p-values under a given threshold (default 0.05)
  bold_labels() 

```












# AE Discont_Day
```{r}
ae_vars <- c(
  "any_ae",
  "terli_ae_abdpain",
  "terli_ae_nausea",
  "terli_ae_diarrhea",
  "terli_ae_volover",
  "terli_ae_brady",
  "terli_7",
  "terli_8",
  "terli_ae_respfail"
)

# Function to summarize median and IQR for each AE variable
summarize_ae <- function(var) {
  final_master %>% 
    group_by(.data[[var]]) %>%
    summarise(
      AE_Var = var,
      Group = as.character(.data[[var]][1]),
      Q1 = quantile(Discont_Day, probs = 0.25, na.rm = TRUE),
      Median = quantile(Discont_Day, probs = 0.5, na.rm = TRUE),
      Q3 = quantile(Discont_Day, probs = 0.75, na.rm = TRUE),
      .groups = "drop"
    )
}

# Apply to each variable and combine results
ae_summary <- map_dfr(ae_vars, summarize_ae) %>% select(AE_Var,Group,Q1,Median,Q3) %>% filter(Group==1)
ae_summary
```


# table1_check
```{r,include=FALSE,message=FALSE,echo=FALSE}

create_table_one(
  all_vars = all_vars,
  cat_vars = categorical_vars,
  data     = final_master,
  strata   = "HRS_criteria_meld",
  output   = "/Users/to909/Desktop/Tables/table1_check_0128_HRS_criteria_meld.csv"
)


```


# table_hospitalization 2026
```{r,include=FALSE}


create_table_one(
  all_vars = hospitalization_course_variables,
  cat_vars = cat_hospitalization_course_variables,
  data     = final_master,
  strata   = "HRS_criteria_meld",
  output   = "/Users/to909/Desktop/Tables/table_hospitalization_0128_HRS_criteria_meld.csv"
)


```

# table_followup 2026
```{r,include=FALSE}
create_table_one(
  all_vars = followup_variables,
  cat_vars = cat_followup_variables,
  data     = final_master,
  strata   = "HRS_criteria_meld",
  output   = "/Users/to909/Desktop/Tables/table_followup_0128_HRS_criteria_meld.csv"
)

```


# table_hrs_clinical 2026
```{r,include=FALSE}
create_table_one(
  all_vars = hrs_clinical_course_variables,
  cat_vars = cat_hrs_clinical_course_variables,
  data     = final_master,
  strata   = "HRS_criteria_meld",
  output   = "/Users/to909/Desktop/Tables/table_hrs_clinical_0128_HRS_criteria_meld.csv"
)
```


# ae by HRS_Criteria 
```{r,echo=FALSE,message=FALSE,warning=FALSE}


ae_vars <- c(
  "any_ae",
  "terli_ae_abdpain",
  "terli_ae_nausea",
  "terli_ae_diarrhea",
  "terli_ae_volover",
  "terli_ae_brady",
  "terli_7",
  "terli_8",
  "terli_ae_respfail"
)

T1_ae <- tableone::CreateTableOne(
    vars       = ae_vars,
    strata     = "HRS_criteria_meld",        # variable to stratify by
    data       = final_master,
    factorVars = ae_vars,      # specify which variables are factors
    addOverall = TRUE,
    includeNA  = FALSE
  )

  # 2) Print TableOne object and convert to data frame
       print1 <- print(
      T1_ae,
      showAllLevels = T,
      missing       = TRUE,
      quote         = FALSE,
      noSpaces      = TRUE,
      printToggle   = FALSE,
      exact = ae_vars[!ae_vars %in% c("terli_ae_respfail","any_ae") ]
    )
 write.csv(print1, file = "/Users/to909/Desktop/Tables/ae by HRS_criteria_meld 2026.csv")
```

