---
title: "Analysis"
author: "Tianqi Ouyang"
date: last-modified
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

This page contains all models and plots from the Terlipressin HARMONY project. Data is loaded from `data_summary.qmd` pipeline. All models use `final_master` as the analysis dataset.

# Setup

```{r libraries}
library(tidyverse)
library(tableone)
library(gtsummary)
library(survival)
library(ggplot2)
library(readxl)
library(survminer)
library(tidycmprsk)
library(ggsurvfit)
library(table1)

final_master <- read_xlsx("/Users/to909/Desktop/Terlipressin projects/Terlipressin/data/final_master_01282026.xlsx")
```

```{r prep, include=FALSE}
# Ensure factor types for key variables
final_master <- final_master %>%
  mutate(
    time_to_death_status_90days = as.integer(time_to_death_status_90days),
    time_to_death_status_90days_cmp = as.factor(time_to_death_status_90days_cmp),
    time_to_transplant_status_90days_1 = ifelse(time_to_transplant_status_90days == 2, 1, 0),
    HRS_reversal_new = as.factor(HRS_reversal_new),
    hrs_responders = as.factor(hrs_responders),
    hrs_responders_cat_2 = as.factor(hrs_responders_cat_2),
    HRS_criteria_3 = as.factor(HRS_criteria_3),
    listed_transplant = as.factor(listed_transplant)
  ) %>%
  drop_na(HRS_reversal_new, hrs_responders)
```

# Kaplan-Meier Survival Curves

## 90-Day Survival by HRS Reversal

```{r km-hrs-reversal, echo=FALSE, fig.height=6}
fit <- survfit(Surv(time_to_death_90days, time_to_death_status_90days) ~ HRS_reversal_new,
               data = final_master)

ggsurvplot(fit, data = final_master, surv.scale = "percent",
  pval = TRUE, pval.coord = c(75, 1), pval.size = 4,
  conf.int = FALSE, xlim = c(0, 90), xlab = "Time (days)",
  break.time.by = 30, tables.theme = theme_cleantable(),
  risk.table = TRUE, risk.table.y.text.col = TRUE,
  risk.table.y.text = TRUE, risk.table.fontsize = 4)
```

## 90-Day Survival by HRS Response Category (3-level)

```{r km-hrs-responders, echo=FALSE, fig.height=6}
fit <- survfit(Surv(time_to_death_90days, time_to_death_status_90days) ~ hrs_responders,
               data = final_master)

ggsurvplot(fit, data = final_master, surv.scale = "percent",
  pval = TRUE, pval.coord = c(75, 1), pval.size = 4,
  conf.int = FALSE, xlim = c(0, 90), xlab = "Time (days)",
  break.time.by = 30, tables.theme = theme_cleantable(),
  risk.table = TRUE, risk.table.y.text.col = TRUE,
  risk.table.y.text = TRUE, risk.table.fontsize = 4)
```

## 90-Day Survival by HRS Responder (Binary)

```{r km-hrs-cat2, echo=FALSE, fig.height=6}
fit <- survfit(Surv(time_to_death_90days, time_to_death_status_90days) ~ hrs_responders_cat_2,
               data = final_master)

ggsurvplot(fit, data = final_master, surv.scale = "percent",
  pval = TRUE, pval.coord = c(75, 1), pval.size = 4,
  conf.int = FALSE, xlim = c(0, 90), xlab = "Time (days)",
  break.time.by = 30, tables.theme = theme_cleantable(),
  risk.table = TRUE, risk.table.y.text.col = TRUE,
  risk.table.y.text = TRUE, risk.table.fontsize = 4)
```

# Logistic Regression: 90-Day Mortality

## Univariate -- HRS Reversal

```{r logistic-uv-death-reversal, echo=FALSE}
final_master %>%
  select(HRS_reversal_new, age, race_2, hispanic, admit_meld_3, listed_transplant,
         time_to_death_status_90days) %>%
  tbl_uvregression(method = glm, method.args = list(family = binomial),
    y = time_to_death_status_90days,
    pvalue_fun = ~style_pvalue(.x, digits = 3), exponentiate = TRUE) %>%
  bold_p(0.05) %>% bold_labels()
```

## Multivariate -- HRS Reversal

```{r logistic-mv-death-reversal, echo=FALSE}
glm(time_to_death_status_90days ~ HRS_reversal_new + age + race_2 + hispanic +
      admit_meld_3 + listed_transplant,
    family = binomial, data = final_master) %>%
  tbl_regression(exp = TRUE) %>% add_n() %>% bold_p(0.05) %>% bold_labels()
```

## Univariate -- HRS Responder (Binary)

```{r logistic-uv-death-cat2, echo=FALSE}
final_master %>%
  select(hrs_responders_cat_2, age, race_2, hispanic, admit_meld_3, listed_transplant,
         time_to_death_status_90days) %>%
  tbl_uvregression(method = glm, method.args = list(family = binomial),
    y = time_to_death_status_90days,
    pvalue_fun = ~style_pvalue(.x, digits = 3), exponentiate = TRUE) %>%
  bold_p(0.05) %>% bold_labels()
```

## Multivariate -- HRS Responder (Binary)

```{r logistic-mv-death-cat2, echo=FALSE}
glm(time_to_death_status_90days ~ hrs_responders_cat_2 + age + race_2 + hispanic +
      admit_meld_3 + listed_transplant,
    family = binomial, data = final_master) %>%
  tbl_regression(exp = TRUE) %>% add_n() %>% bold_p(0.05) %>% bold_labels()
```

# Logistic Regression: 90-Day Transplant

## Univariate -- HRS Reversal

```{r logistic-uv-tx-reversal, echo=FALSE}
final_master %>%
  select(HRS_reversal_new, age, race_2, hispanic, admit_meld_3, transplant_outcome) %>%
  tbl_uvregression(method = glm, method.args = list(family = binomial),
    y = transplant_outcome,
    pvalue_fun = ~style_pvalue(.x, digits = 3), exponentiate = TRUE) %>%
  bold_p(0.05) %>% bold_labels()
```

## Multivariate -- HRS Reversal

```{r logistic-mv-tx-reversal, echo=FALSE}
glm(transplant_outcome ~ HRS_reversal_new + age + race_2 + hispanic + admit_meld_3,
    family = binomial, data = final_master) %>%
  tbl_regression(exp = TRUE) %>% add_n() %>% bold_p(0.05) %>% bold_labels()
```

## Univariate -- HRS Responder (Binary)

```{r logistic-uv-tx-cat2, echo=FALSE}
final_master %>%
  select(hrs_responders_cat_2, age, race_2, hispanic, admit_meld_3, transplant_outcome) %>%
  tbl_uvregression(method = glm, method.args = list(family = binomial),
    y = transplant_outcome,
    pvalue_fun = ~style_pvalue(.x, digits = 3), exponentiate = TRUE) %>%
  bold_p(0.05) %>% bold_labels()
```

## Multivariate -- HRS Responder (Binary)

```{r logistic-mv-tx-cat2, echo=FALSE}
glm(transplant_outcome ~ hrs_responders_cat_2 + age + race_2 + hispanic + admit_meld_3,
    family = binomial, data = final_master) %>%
  tbl_regression(exp = TRUE) %>% add_n() %>% bold_p(0.05) %>% bold_labels()
```

## Transplant -- Listed Patients Only (HRS Reversal)

```{r logistic-tx-listed-reversal, echo=FALSE}
glm(transplant_outcome ~ HRS_reversal_new + age + race_2 + hispanic + admit_meld_3,
    family = binomial, data = final_master %>% filter(listed_transplant == 1)) %>%
  tbl_regression(exp = TRUE) %>% add_n() %>% bold_p(0.05) %>% bold_labels()
```

## Transplant -- Listed Patients Only (HRS Responder)

```{r logistic-tx-listed-cat2, echo=FALSE}
glm(transplant_outcome ~ hrs_responders_cat_2 + age + race_2 + hispanic + admit_meld_3,
    family = binomial, data = final_master %>% filter(listed_transplant == 1)) %>%
  tbl_regression(exp = TRUE) %>% add_n() %>% bold_p(0.05) %>% bold_labels()
```

# Cox Proportional Hazards: 90-Day Mortality

## Univariate -- HRS Reversal

```{r cox-uv-reversal, echo=FALSE}
final_master %>% filter(time_to_death_90days >= 0) %>%
  select(HRS_reversal_new, age, race_2, hispanic, admit_meld_3, listed_transplant,
         time_to_death_90days, time_to_death_status_90days) %>%
  tbl_uvregression(method = coxph,
    y = Surv(time_to_death_90days, time_to_death_status_90days),
    pvalue_fun = ~style_pvalue(.x, digits = 3), exponentiate = TRUE) %>%
  bold_p(0.05) %>% bold_labels()
```

## Multivariate -- HRS Reversal

```{r cox-mv-reversal, echo=FALSE}
coxph(Surv(time_to_death_90days, time_to_death_status_90days) ~
        HRS_reversal_new + age + race_2 + hispanic + admit_meld_3 + listed_transplant,
      data = final_master) %>%
  tbl_regression(exp = TRUE) %>% add_n() %>% bold_p(0.05) %>% bold_labels()
```

## Univariate -- HRS Responder (Binary)

```{r cox-uv-cat2, echo=FALSE}
final_master %>%
  select(hrs_responders_cat_2, age, race_2, hispanic, admit_meld_3, listed_transplant,
         time_to_death_90days, time_to_death_status_90days) %>%
  tbl_uvregression(method = coxph,
    y = Surv(time_to_death_90days, time_to_death_status_90days),
    pvalue_fun = ~style_pvalue(.x, digits = 3), exponentiate = TRUE) %>%
  bold_p(0.05) %>% bold_labels()
```

## Multivariate -- HRS Responder (Binary)

```{r cox-mv-cat2, echo=FALSE}
coxph(Surv(time_to_death_90days, time_to_death_status_90days) ~
        hrs_responders_cat_2 + age + race_2 + hispanic + admit_meld_3 + listed_transplant,
      data = final_master) %>%
  tbl_regression(exp = TRUE) %>% add_n() %>% bold_p(0.05) %>% bold_labels()
```

# Cox Proportional Hazards: 90-Day Transplant

## Multivariate -- HRS Reversal

```{r cox-tx-reversal, echo=FALSE}
coxph(Surv(time_to_transplant_90days, time_to_transplant_status_90days_1) ~
        HRS_reversal_new + age + race_2 + hispanic + admit_meld_3,
      data = final_master) %>%
  tbl_regression(exp = TRUE) %>% add_n() %>% bold_p(0.05) %>% bold_labels()
```

## Multivariate -- HRS Responder (Binary)

```{r cox-tx-cat2, echo=FALSE}
coxph(Surv(time_to_transplant_90days, time_to_transplant_status_90days_1) ~
        hrs_responders_cat_2 + age + race_2 + hispanic + admit_meld_3,
      data = final_master) %>%
  tbl_regression(exp = TRUE) %>% add_n() %>% bold_p(0.05) %>% bold_labels()
```

# Fine-Gray Competing Risk: 90-Day (Death vs. Transplant)

## All Patients

### Univariate -- HRS Responder (failcode=1: Death)

```{r fg-uv-cat2-death, echo=FALSE}
final_master %>%
  select(hrs_responders_cat_2, age, race_2, hispanic, admit_meld_3,
         time_to_death_90days_cmp, time_to_death_status_90days_cmp) %>%
  tbl_uvregression(method = tidycmprsk::crr,
    method.args = list(failcode = 1, cencode = 0),
    y = Surv(time_to_death_90days_cmp, time_to_death_status_90days_cmp),
    pvalue_fun = ~style_pvalue(.x, digits = 3), exponentiate = TRUE)
```

### Multivariate -- HRS Responder (failcode=1: Death)

```{r fg-mv-cat2-death, echo=FALSE}
tidycmprsk::crr(Surv(time_to_death_90days_cmp, time_to_death_status_90days_cmp) ~
  hrs_responders_cat_2 + age + race_2 + hispanic + admit_meld_3,
  failcode = 1, cencode = 0, data = final_master) %>%
  tbl_regression(exp = TRUE) %>% add_n() %>% bold_p(0.05) %>% bold_labels()
```

### Univariate -- HRS Responder (failcode=2: Transplant)

```{r fg-uv-cat2-tx, echo=FALSE}
final_master %>%
  select(hrs_responders_cat_2, age, race_2, hispanic, admit_meld_3,
         time_to_death_90days_cmp, time_to_death_status_90days_cmp) %>%
  tbl_uvregression(method = tidycmprsk::crr,
    method.args = list(failcode = 2, cencode = 0),
    y = Surv(time_to_death_90days_cmp, time_to_death_status_90days_cmp),
    pvalue_fun = ~style_pvalue(.x, digits = 3), exponentiate = TRUE) %>%
  bold_p(0.05) %>% bold_labels()
```

### Multivariate -- HRS Responder (failcode=2: Transplant)

```{r fg-mv-cat2-tx, echo=FALSE}
tidycmprsk::crr(Surv(time_to_death_90days_cmp, time_to_death_status_90days_cmp) ~
  hrs_responders_cat_2 + age + race_2 + hispanic + admit_meld_3,
  failcode = 2, cencode = 0, data = final_master) %>%
  tbl_regression(exp = TRUE) %>% add_n() %>% bold_p(0.05) %>% bold_labels()
```

### Multivariate -- HRS Reversal (failcode=1: Death)

```{r fg-mv-reversal-death, echo=FALSE}
tidycmprsk::crr(Surv(time_to_death_90days_cmp, time_to_death_status_90days_cmp) ~
  HRS_reversal_new + age + race_2 + hispanic + admit_meld_3,
  failcode = 1, cencode = 0, data = final_master) %>%
  tbl_regression(exp = TRUE) %>% add_n() %>% bold_p(0.05) %>% bold_labels()
```

### Multivariate -- HRS Reversal (failcode=2: Transplant)

```{r fg-mv-reversal-tx, echo=FALSE}
tidycmprsk::crr(Surv(time_to_death_90days_cmp, time_to_death_status_90days_cmp) ~
  HRS_reversal_new + age + race_2 + hispanic + admit_meld_3,
  failcode = 2, cencode = 0, data = final_master) %>%
  tbl_regression(exp = TRUE) %>% add_n() %>% bold_p(0.05) %>% bold_labels()
```

## Subgroup: Futility Criteria Met (HRS_criteria_3 == 1)

### Multivariate -- HRS Responder (failcode=1: Death)

```{r fg-criteria1-cat2-death, echo=FALSE}
tidycmprsk::crr(Surv(time_to_death_90days_cmp, time_to_death_status_90days_cmp) ~
  hrs_responders_cat_2 + age + race_2 + hispanic + admit_meld_3,
  failcode = 1, cencode = 0,
  data = final_master %>% filter(HRS_criteria_3 == 1)) %>%
  tbl_regression(exp = TRUE) %>% add_n() %>% bold_p(0.05) %>% bold_labels()
```

### Multivariate -- HRS Reversal (failcode=1: Death)

```{r fg-criteria1-reversal-death, echo=FALSE}
tidycmprsk::crr(Surv(time_to_death_90days_cmp, time_to_death_status_90days_cmp) ~
  HRS_reversal_new + age + race_2 + hispanic + admit_meld_3,
  failcode = 1, cencode = 0,
  data = final_master %>% filter(HRS_criteria_3 == 1)) %>%
  tbl_regression(exp = TRUE) %>% add_n() %>% bold_p(0.05) %>% bold_labels()
```

## Subgroup: Futility Criteria Not Met (HRS_criteria_3 == 0)

### Multivariate -- HRS Responder (failcode=1: Death)

```{r fg-criteria0-cat2-death, echo=FALSE}
tidycmprsk::crr(Surv(time_to_death_90days_cmp, time_to_death_status_90days_cmp) ~
  hrs_responders_cat_2 + age + race_2 + hispanic + admit_meld_3,
  failcode = 1, cencode = 0,
  data = final_master %>% filter(HRS_criteria_3 == 0)) %>%
  tbl_regression(exp = TRUE) %>% add_n() %>% bold_p(0.05) %>% bold_labels()
```

### Multivariate -- HRS Reversal (failcode=1: Death)

```{r fg-criteria0-reversal-death, echo=FALSE}
tidycmprsk::crr(Surv(time_to_death_90days_cmp, time_to_death_status_90days_cmp) ~
  HRS_reversal_new + age + race_2 + hispanic + admit_meld_3,
  failcode = 1, cencode = 0,
  data = final_master %>% filter(HRS_criteria_3 == 0)) %>%
  tbl_regression(exp = TRUE) %>% add_n() %>% bold_p(0.05) %>% bold_labels()
```

## Subgroup: Listed for Transplant

### Multivariate -- HRS Responder (failcode=2: Transplant)

```{r fg-listed-cat2-tx, echo=FALSE}
tidycmprsk::crr(Surv(time_to_death_90days_cmp, time_to_death_status_90days_cmp) ~
  hrs_responders_cat_2 + age + race_2 + hispanic + admit_meld_3,
  failcode = 2, cencode = 0,
  data = final_master %>% filter(listed_transplant == 1)) %>%
  tbl_regression(exp = TRUE) %>% add_n() %>% bold_p(0.05) %>% bold_labels()
```

### Multivariate -- HRS Reversal (failcode=2: Transplant)

```{r fg-listed-reversal-tx, echo=FALSE}
tidycmprsk::crr(Surv(time_to_death_90days_cmp, time_to_death_status_90days_cmp) ~
  HRS_reversal_new + age + race_2 + hispanic + admit_meld_3,
  failcode = 2, cencode = 0,
  data = final_master %>% filter(listed_transplant == 1)) %>%
  tbl_regression(exp = TRUE) %>% add_n() %>% bold_p(0.05) %>% bold_labels()
```

## Subgroup: Not Listed for Transplant

### Multivariate -- HRS Responder (failcode=2: Transplant)

```{r fg-notlisted-cat2-tx, echo=FALSE}
tidycmprsk::crr(Surv(time_to_death_90days_cmp, time_to_death_status_90days_cmp) ~
  hrs_responders_cat_2 + age + race_2 + hispanic + admit_meld_3,
  failcode = 2, cencode = 0,
  data = final_master %>% filter(listed_transplant == 0)) %>%
  tbl_regression(exp = TRUE) %>% add_n() %>% bold_p(0.05) %>% bold_labels()
```

### Multivariate -- HRS Reversal (failcode=2: Transplant)

```{r fg-notlisted-reversal-tx, echo=FALSE}
tidycmprsk::crr(Surv(time_to_death_90days_cmp, time_to_death_status_90days_cmp) ~
  HRS_reversal_new + age + race_2 + hispanic + admit_meld_3,
  failcode = 2, cencode = 0,
  data = final_master %>% filter(listed_transplant == 0)) %>%
  tbl_regression(exp = TRUE) %>% add_n() %>% bold_p(0.05) %>% bold_labels()
```

# Cross-Tabulations

## SCr Category by HRS Reversal

```{r crosstab-scr-reversal, echo=FALSE}
final_master %>%
  mutate(scr_category = cut(scr_terli_day0,
    breaks = c(-Inf, 1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5, Inf),
    labels = c("<1.5", "1.5-2", "2-2.5", "2.5-3", "3-3.5", "3.5-4", "4-4.5", "4.5-5", ">5"),
    right = FALSE)) %>%
  count(scr_category, HRS_reversal_new) %>%
  pivot_wider(names_from = HRS_reversal_new, values_from = n, values_fill = 0) %>%
  knitr::kable(caption = "SCr Category at Day 0 vs HRS Reversal")
```

## MELD 3.0 Quintiles by HRS Reversal

```{r crosstab-meld-reversal, echo=FALSE}
final_master %>% drop_na(admit_meld_3_raw) %>%
  mutate(meld_quintile = cut(admit_meld_3_raw,
    breaks = quantile(admit_meld_3_raw, probs = seq(0, 1, 0.2), na.rm = TRUE),
    include.lowest = TRUE, labels = paste0("Q", 1:5))) %>%
  count(meld_quintile, HRS_reversal_new) %>%
  pivot_wider(names_from = HRS_reversal_new, values_from = n, values_fill = 0) %>%
  knitr::kable(caption = "MELD 3.0 Quintile vs HRS Reversal")
```

# AE Summary by Discontinuation Day

```{r ae-discont-day, echo=FALSE}
ae_vars <- c("any_ae", "terli_ae_abdpain", "terli_ae_nausea", "terli_ae_diarrhea",
             "terli_ae_volover", "terli_ae_brady", "terli_7", "terli_8", "terli_ae_respfail")

map_dfr(ae_vars, function(var) {
  final_master %>%
    filter(.data[[var]] == 1) %>%
    summarise(
      AE = var,
      N = n(),
      Q1 = quantile(Discont_Day, 0.25, na.rm = TRUE),
      Median = median(Discont_Day, na.rm = TRUE),
      Q3 = quantile(Discont_Day, 0.75, na.rm = TRUE))
}) %>% knitr::kable(caption = "Discontinuation Day by AE Type (among those with AE)")
```
