---
title: "Example"
author: "Tianqi Ouyang"
date: last-modified
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(gtsummary)
library(survival)
library(survminer)
library(tidycmprsk)
library(ggsurvfit)
library(readxl)

final_master <- read_xlsx("/Users/to909/Desktop/Terlipressin projects/Terlipressin/data/final_master_01282026.xlsx")

final_master <- final_master %>%
  mutate(
    time_to_death_status_90days = as.integer(time_to_death_status_90days),
    time_to_death_status_90days_cmp = as.factor(time_to_death_status_90days_cmp),
    HRS_reversal_new = as.factor(HRS_reversal_new),
    hrs_responders_cat_2 = as.factor(hrs_responders_cat_2)
  ) %>%
  drop_na(HRS_reversal_new, hrs_responders)
```

# Kaplan-Meier: 90-Day Survival by HRS Reversal

```{r km-plot, fig.height=6}
fit <- survfit(
  Surv(time_to_death_90days, time_to_death_status_90days) ~ HRS_reversal_new,
  data = final_master
)

ggsurvplot(
  fit,
  data = final_master,
  surv.scale = "percent",
  pval = TRUE,
  pval.coord = c(75, 1),
  pval.size = 4,
  conf.int = FALSE,
  xlim = c(0, 90),
  xlab = "Time (days)",
  break.time.by = 30,
  tables.theme = theme_cleantable(),
  risk.table = TRUE,
  risk.table.y.text.col = TRUE,
  risk.table.y.text = TRUE,
  risk.table.fontsize = 4
)
```

# Logistic Regression: 90-Day Mortality

Multivariate logistic regression with HRS reversal as primary exposure, adjusted for age, race, ethnicity, MELD 3.0, and transplant listing status.

```{r logistic-model}
model_logistic <- glm(
  time_to_death_status_90days ~
    HRS_reversal_new + age + race_2 + hispanic + admit_meld_3 + listed_transplant,
  family = binomial,
  data = final_master
)

tbl_regression(model_logistic, exponentiate = TRUE) %>%
  add_n() %>%
  bold_p(0.05) %>%
  bold_labels()
```

# Fine-Gray Competing Risk: 90-Day Mortality (Death vs. Transplant)

Multivariate Fine-Gray competing risk model. Death (`failcode = 1`) is the event of interest; transplant (`failcode = 2`) is the competing event; `cencode = 0` is censored.

```{r fine-gray-model}
model_fg <- tidycmprsk::crr(
  Surv(time_to_death_90days_cmp, time_to_death_status_90days_cmp) ~
    HRS_reversal_new + age + race_2 + hispanic + admit_meld_3,
  failcode = 1,
  cencode = 0,
  data = final_master
)

tbl_regression(model_fg, exponentiate = TRUE) %>%
  add_n() %>%
  bold_p(0.05) %>%
  bold_labels()
```
